---
title: "Dynamic Deal Scoring EDA"
author: "Snoopy Quartet"
date: "24 March 2021"
output: html_document
---

# Import libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(GGally)
library(lubridate)
library(dplyr)
library(patchwork)
library(gridExtra)
library(Cairo)
library(grid)
library(zoo)
library(purrr)
library(xts)
library(reshape2)
library(imputeTS)
library(RColorBrewer)
library(kableExtra)
library(scales)
library(grid)
library(schoolmath)
```

## Define quantile filtering function
```{r}
filter_by_quantile <- function(param, lower=0.01, upper=0.99) {
    return(quantile(param, lower, na.rm=T) < param & param < quantile(param, upper, na.rm=T))
}
```

## Load data set into memory
```{r}
df <- read.csv("./dataset/LUMEN_DS.csv",                 
               header=TRUE,
               stringsAsFactors=FALSE,
               sep="|",
               quote="",
               encoding="UCS-2LE",
               fileEncoding="UCS-2LE")
```

## Get rid of qutoes
```{r}
df <- as.data.frame(sapply(df, function(x) gsub("\"", "", x)))
```

## Change column names, define types of columns 
```{r}
colnames(df) <- c("manufacturing_region", "manufacturing_location_code", "intercompany", "customer_id", "customer_industry", "customer_region", "customer_first_invoice_date", "top_customer_group", "item_code", "product_family", "product_group", "price_last_modified_date_in_the_erp", "born_on_date", "make_vs_buy", "sales_channel_internal", "sales_channel_external", "sales_channel_grouping", "invoice_date", "invoice_num", "invoice_line_num", "order_date", "order_num", "order_line_num", "invoiced_qty_shipped", "ordered_qty", "invoiced_price", "invoiced_price_tx", "cost_of_part", "material_cost_of_part", "labor_cost_of_part", "overhead_cost_of_part", "gm", "num_of_unique_products_on_a_quote")

factor_cols <- c("manufacturing_region", "manufacturing_location_code", "intercompany", "customer_id", "customer_industry", "customer_region", "top_customer_group", "item_code", "product_family", "product_group", "make_vs_buy", "sales_channel_internal", "sales_channel_external", "sales_channel_grouping", "invoice_num", "invoice_line_num", "order_num", "order_line_num")

date_cols <- c("born_on_date", "invoice_date", "order_date")
datetime_cols <- c("customer_first_invoice_date", "price_last_modified_date_in_the_erp")

numeric_cols <- c("invoiced_qty_shipped", "ordered_qty", "invoiced_price", "invoiced_price_tx", "cost_of_part", "material_cost_of_part", "labor_cost_of_part", "overhead_cost_of_part", "gm", "num_of_unique_products_on_a_quote")

df <- df %>% 
    mutate(across(everything(), ~na_if(., "NaN"))) %>% 
    mutate(across(.fns = ~na_if(., ""))) %>%
    mutate(across(all_of(factor_cols), as.factor),
           across(all_of(date_cols), lubridate::ymd),
           across(all_of(datetime_cols), lubridate::date),
           across(all_of(numeric_cols), as.character),
           across(all_of(numeric_cols), as.numeric))
```

## Get general information about data set
```{r}
head(df)
```

```{r}
glimpse(df)
```

## Dataset irregularities

### Missing values
```{r}
df %>%
    summarise_all(funs(sum(is.na(.)))) %>% 
    melt -> NA_counts_df

NA_counts_df %>% 
    ggplot(aes(x=reorder(variable, -value), y=value, colour=variable)) +
    geom_bar(stat="identity", color="blue", fill="white") + 
    theme_bw() + 
    theme(axis.text.x=element_text(angle=90, vjust=0.5, size=6)) + 
    labs(x="Column name", y="Missing values count") +
    scale_y_continuous(labels=comma_format(big.mark=",", decimal.mark = "."), breaks=seq(0, max(NA_counts_df$value) + 100000, 100000)) -> plot 

ggsave("./plots/NA_distribution.png", plot, width = 15, height = 10)
```

### price_last_modified_in_the_erp percentage of missing rows
```{r}
count <- NA_counts_df %>% filter(variable == "price_last_modified_date_in_the_erp") %>% select(value) %>% pull
count / nrow(df)
```

### Negative or zero values
```{r}
df %>% select(cost_of_part) %>% drop_na %>%  filter(cost_of_part < 0) %>% pull %>% length %>% paste0("cost_of_part negative: ", .)

df %>% select(cost_of_part) %>% drop_na %>%  filter(cost_of_part == 0) %>% pull %>% length %>% paste0("cost_of_part zero: ", .)

df %>% select(invoiced_price) %>% drop_na %>%  filter(invoiced_price < 0) %>% pull %>% length %>% paste0("invoiced_price negative: ", .)

df %>% select(invoiced_price) %>% drop_na %>%  filter(invoiced_price == 0) %>% pull %>% length %>% paste0("invoiced_price zero: ", .)

df %>% select(gm) %>% drop_na %>% filter(gm < 0) %>% pull %>% length %>% paste0("gm negative: ", .)

df %>% select(gm) %>% drop_na %>%  filter(gm > 1) %>% pull %>% length %>% paste0("gm higher than 1: ", .)

df %>% select(ordered_qty) %>% drop_na %>% filter(ordered_qty < 0) %>% pull %>% length %>% paste0("ordered_qty negative: ", .)

df %>% select(ordered_qty) %>% drop_na %>% filter(ordered_qty == 0) %>% pull %>% length %>% paste0("ordered_qty zero: ", .)

df %>% select(invoiced_qty_shipped) %>% drop_na %>% filter(invoiced_qty_shipped < 0) %>% pull %>% length %>% paste0("invoiced_qty_shipped negative: ", .)

df %>% select(invoiced_qty_shipped) %>% drop_na %>% filter(invoiced_qty_shipped == 0) %>% pull %>% length %>% paste0("invoiced_qty_shipped zero: ", .)
```

### When is gm missing?
```{r}
df %>% 
    filter(invoiced_price == 0 | is.na(invoiced_price) | is.na(cost_of_part)) %>% pull %>% length -> num_1

df %>% 
    filter(is.na(gm)) %>% select(gm) %>% pull %>% length -> num_2

print(num_1 == num_2)
```

### What item codes have ordered quantity equal to zero?
```{r}
df %>% filter(ordered_qty == 0) %>% select(item_code) %>% group_by(item_code) %>% tally %>% arrange(desc(n)) 
```

### What item codes have invoiced quantity shipped equal to zero?
```{r}
df %>% filter(invoiced_qty_shipped == 0) %>% select(item_code, customer_region) %>% group_by(item_code, customer_region) %>% tally %>% arrange(desc(n)) 
```

### Column make vs buy - merge into only make and buy
```{r}
df %>% select(make_vs_buy) %>% unique
```

## Order example
```{r}
df %>% filter(order_num == "577108")
```

## Number of unique products
```{r}
df %>% 
    select(item_code) %>% 
    unique %>% 
    pull %>% 
    length
```

## Unique regions
```{r}
regions <- df %>% select(customer_region) %>% filter(!is.na(customer_region)) %>% unique %>% pull
```

## 10 most sold products everywhere, 10 most sold products by customer region
```{r}
df %>%
    select(item_code) %>% 
    filter(!is.na(item_code)) %>%
    count(item_code, sort=T) %>% 
    top_n(10, n) %>% kable

item_freq_table_by_region <- function(region) {
    df %>%
        select(item_code, customer_region) %>% 
        filter(!is.na(item_code)) %>%
        group_by(customer_region) %>% 
        count(item_code, customer_region, sort=T) %>% 
        top_n(10, n) %>% 
        filter(customer_region == region) %>% kable
}

plots <- map(regions, function(region) item_freq_table_by_region(region))
plots[[1]]
plots[[2]]
plots[[3]]
```

## 10 most expensive products with their invoice price everywhere
```{r}
df %>%
    select(item_code, invoiced_price) %>% 
    filter(!is.na(item_code)) %>% 
    top_n(10, invoiced_price) %>% 
    arrange(desc(invoiced_price)) %>% kable
```

## Relationship between manufacturing_region, customer_region and gm
```{r}
gm_barplot <- function(x_variable) {
    df %>% 
        select({{x_variable}}, gm) %>% 
        group_by({{x_variable}}) %>% 
        filter(filter_by_quantile(gm)) %>% 
        summarise(mean_gm=mean(gm, na.rm=T)) %>% 
        ggplot(aes(x={{x_variable}}, y=mean_gm), fill={{x_variable}}) +
        geom_bar(stat="identity", fill="forestgreen") + 
        theme_bw()
}

gm_barplot(manufacturing_region)
gm_barplot(customer_region)
```

```{r, warning=F}
df %>% 
    select(manufacturing_region, customer_region, gm) %>% 
    filter(!is.na(manufacturing_region) & !is.na(customer_region)) %>% 
    group_by(manufacturing_region, customer_region) %>% 
    filter(filter_by_quantile(gm)) %>% 
    summarise(mean_gm=mean(gm, na.rm=T)) %>% 
    mutate(manufacturer_customer=
               paste0(paste0(paste0("manufacturer=", manufacturing_region), "\n"),
                      paste0("customer=", customer_region))) %>% 
    ggplot(aes(x=manufacturer_customer, y=mean_gm), fill=manufacturer_customer) +
    geom_bar(stat="identity", fill="forestgreen") + 
    theme_bw() +
    theme(axis.text.x=element_text(angle=45, vjust=0.5, size=6))

df %>% 
    select(manufacturing_region, customer_region, gm) %>% 
    filter(!is.na(manufacturing_region) & !is.na(customer_region)) %>% 
    group_by(manufacturing_region, customer_region) %>% 
    filter(filter_by_quantile(gm)) %>% 
    summarise(mean_gm=mean(gm, na.rm=T)) %>% 
    mutate(manufacturer_customer=
               paste0(paste0(paste0("manufacturer=", manufacturing_region), "\n"),
                      paste0("customer=", customer_region))) %>% 
    filter(manufacturer_customer != "manufacturer=Asia\ncustomer=Europe") -> df_filtered

df_filtered %>%    
    ggplot(aes(x=manufacturer_customer, y=mean_gm), fill=manufacturer_customer) +
    geom_bar(stat="identity", fill="forestgreen") + 
    theme_bw() +
    theme(axis.text.x=element_text(angle=45, vjust=0.5, size=6)) + 
    scale_y_continuous(breaks=seq(-4, 1, 0.2)) 
```

## Manufacturer-customer percentage relation, realtionship with make_vs_buy
```{r}
df %>% 
    ggplot(aes(x=manufacturing_region, fill=customer_region)) +
    geom_bar(position="fill", color="white") +
    scale_fill_brewer(palette="Dark2") + 
    theme_bw() + 
    theme(axis.title = element_text(size = 15), 
          legend.title = element_text(size= 15))

df %>% 
    ggplot(aes(x=manufacturing_region, fill=make_vs_buy)) +
    geom_bar(position="fill", color="white") +
    scale_fill_brewer(palette="Paired") + 
    theme_bw() + 
    theme(axis.title = element_text(size = 15), 
          legend.title = element_text(size= 15))
```

## Invoice price distribution depending on manufactured_region and customer_region
```{r}
df %>% 
    select(manufacturing_region, invoiced_price) %>% 
    filter(!is.na(manufacturing_region)) %>% 
    filter(filter_by_quantile(invoiced_price, 0.05, 0.95)) %>%  
    ggplot(aes(x=manufacturing_region, y=invoiced_price)) + 
    geom_boxplot(aes(fill=manufacturing_region)) +
    # scale_y_continuous(limits = c(0, 50)) +
    theme_bw() +
    theme(legend.position = "bottom", legend.title=element_blank())

df %>% 
    select(customer_region, invoiced_price) %>% 
    filter(!is.na(customer_region)) %>% 
    filter(filter_by_quantile(invoiced_price, 0.05, 0.95)) %>%  
    ggplot(aes(x=customer_region, y=invoiced_price)) + 
    geom_boxplot(aes(fill=customer_region)) +
    # scale_y_continuous(limits = c(0, 50)) +
    theme_bw() +
    theme(legend.position = "bottom", legend.title=element_blank())
```

## Manufacturing locations
```{r}
# Manufacturing region and its location codes counts
df %>% 
    select(manufacturing_region, manufacturing_location_code) %>% 
    filter(!is.na(manufacturing_region)) %>% 
    group_by(manufacturing_region) %>% 
    count(manufacturing_region, manufacturing_location_code, sort=T) 

# Customer region and manufacturing location codes counts
df %>% 
    select(customer_region, manufacturing_location_code) %>% 
    filter(!is.na(customer_region)) %>% 
    group_by(customer_region) %>% 
    count(customer_region, manufacturing_location_code, sort=T) 

# Cost of part difference depending on manufacturing location
plot_violin_cost <- function(region) {
    df %>%
        filter(manufacturing_region == region) %>% 
        select(manufacturing_location_code, cost_of_part) %>% 
        filter(!is.na(manufacturing_location_code)) %>% 
        filter(filter_by_quantile(cost_of_part, 0.05, 0.95)) %>%  
        ggplot(aes(x=manufacturing_location_code, y=cost_of_part)) + 
        geom_violin(aes(fill=manufacturing_location_code)) +
        scale_y_continuous(limits=c(0, 250)) +
        theme_bw() +
        theme(legend.position="bottom", legend.title=element_blank(), plot.title=element_text(hjust=0.5)) + 
        ggtitle(paste0("Region=", region))
}

cost_location_plots <- map(regions, function(region) plot_violin_cost(region))

cost_location_plots[[1]]
cost_location_plots[[2]]
cost_location_plots[[3]]
```
