---
title: "EDA - Part III"
author: "Josip Domazet"
date: "5/7/2021"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Is cost of part changing?
Check whether price components are changing
I'll use one specific item_code
```{r}
dat %>% filter(item_code == 23254681) %>% view("spec")
```

Maybe for multiple items?
```{r}
dat %>% filter(item_code  %in% c("1291")) %>% 
  ggplot(aes(invoice_date, cost_of_part)) +
  geom_point(aes(size = invoiced_qty_shipped), color = "red", alpha = 0.2) +
  geom_point(aes(invoice_date, invoiced_price), color = "blue")
```
we should remove invoiced_price == 0 because sometimes it's due to 
internal company policies.
But why is cost of part sometimes equal to zero? Is it also due to
internal company policies? 
Q: How can something be free to produce? 
A: Check make_vs_buy. Column. It's buy.

##Undefined gross margin 
```{r}
{
dat %>% 
  filter(invoiced_price == 0 | is.na(invoiced_price) | is.na(cost_of_part)) %>% 
  nrow() } ==  {
dat %>% 
  filter(is.na(gm)) %>% 
  nrow()
  }
```
Gross margin is undefined in three cases (not mutually exclusive):
1. invoiced_price == 0 
2. invoiced_price not defined
3. cost_of_part not defined. **possible transportation! ** 

Let's check which items have undefined gross margins.
Since we're segmenting rows into gross margin buckets, 
having undefined gross margin is of no use for us.

13923 items have at least one invoice line in which they
don't have defined gross margin.
```{r}
dat %>% 
  filter(is.na(gm)) %>% 
  count(item_code, sort = TRUE) %>% 
  mutate(item_code = fct_reorder(item_code, n)) %>% 
  slice_max(n, n = 50) %>%  
  ggplot(aes(n, item_code)) +
  geom_col()
```
Top items with NA gross margin: by the number of rows:
1. BOY485-NPI (free item?!?!?!?!?!?!?!?!?)
2. /C
3. TRANSPORTKOSTEN
4. /LTI
5. SMSKID
```{r}
top_items_na_gm <- c("BOY485-NPI", "/C", "TRANSPORTKOSTEN",
                     "/LTI", "SMSKID", "LGMC-000203",
                     "LGSKID", "SAMPLE-MPCS", "SAMPLE-EACH",
                     "BOY485-SAMPLES")
```


###Transportation items
Items with biggest number of rows with undefined gross margin are
candidates for transportation items.

BOY385-NPI has 155916 rows. Almost all of them have invoiced_price equal to 0.
TRASNPOSRTKOSTEN has 7947 rows. Only 1 didn't have invoiced price equal to 0.
We can remove rows which don't have invoiced price equal to 0.
```{r}
dat %>% 
  filter(item_code == "BOY485-NPI") %>% 
  ggplot(aes(cost_of_part, invoiced_price)) +
  geom_point() 
```

```{r}
dat %>% 
  filter(item_code == "TRANSPORTKOSTEN") %>% 
  ggplot(aes(cost_of_part, invoiced_price)) +
  geom_point()
# one and only one row doesn't have invoiced_price equal to 0
```

```{r}
dat %>% 
    filter(item_code %in% top_items_na_gm) %>% 
  group_by(item_code) %>%
  summarise(total_rows = n(),
            cost_of_part_na = sum(cost_of_part == 0 | is.na(cost_of_part)),
            mean_cost_of_part = mean(cost_of_part, na.rm = TRUE),
            pct_cost_of_part_na = cost_of_part_na / total_rows,
            ordered_qty = sum(ordered_qty == 0 | is.na(ordered_qty)),
            pct_ordered_qty_na = ordered_qty / total_rows,
            make_vs_buy_na = sum(is.na(make_vs_buy)),
            pct_make_vs_buy_na = make_vs_buy_na / total_rows,
            born_on_date_na = sum(is.na(born_on_date)),
            pct_born_on_date_na = born_on_date_na / total_rows,
            product_group_na = sum(is.na(product_group)),
            pct_product_group_by = product_group_na / total_rows
            ) %>% 
  arrange(desc(total_rows)) %>% 
  select(item_code, total_rows, pct_cost_of_part_na, pct_ordered_qty_na,
         pct_make_vs_buy_na, pct_born_on_date_na, pct_product_group_by)
```

TRANSPORTKOSTEN has defined ordered quantities, but "/C" and "/LTI" don't.
Furthermore, TRANSPORTKOSTEN has NA for make_vs_buy, while /C and /LTI have
make_vs_buy as MANUFACTURED.
##Gross margin greater than 1
It doesn't make sense.
Either:
- negative cost_of_part (somebody paid the company to produce)
- negative invoiced_price (the company paid someone to buy)

Only 96 data set rows have gm greater than 1.
0.074 promil

##Negative gross margins

It happens when the invoiced price is far smaller than
cost of part.

8.6% of rows have negative gross margin.
```{r}
dat %>% 
  filter(gm < 0) %>% 
  mutate(shipped_bin = ggplot2::cut_number(invoiced_qty_shipped, n = 10)) %>% 
  ggplot(aes(cost_of_part, invoiced_price, color = shipped_bin)) + 
  geom_point() +
  labs(
    x = "Cost of part",
    y = "Invoiced price"
  )

# (cost_of_part, invoiced_price)
# (65316.07, 65038)
```

## Gross margin by customer region
```{r}
dat %>%
  filter(between(gm, 0, 1)) %>% 
  ggplot(aes(gm, customer_region)) +
  geom_density_ridges() +
  labs(
    x = "Gross margin",
    y = "Customer region"
  ) 
```


# Quantities

**linear scale**
```{r}
dat %>% 
  filter(!is.na(order_line_num)) %>% 
  select(order_line_num, ordered_qty) %>% 
  distinct() -> order_line_qty_distinct
# perhaps some transportation items sometimes have ordered quantity equal to zero
# and sometimes NA

order_line_qty_distinct %>% 
  mutate(qty_bin = case_when(
    ordered_qty < 0 ~ "negative",
    ordered_qty == 0 ~ "exactly zero",
    ordered_qty > 0 & ordered_qty < 10 ~ "between 0 and 10",
    between(ordered_qty, 10, 100) ~ "between 10 and 100",
    between(ordered_qty, 100, 1000) ~ "between 100 and 1000",
    ordered_qty > 1000 ~ "more than 1000"
  )) %>% 
  group_by(qty_bin) %>% 
  tally() %>% 
  mutate(n = 100*n / sum(n))

```

```{r}
{
order_line_qty_distinct %>% 
  filter(between(ordered_qty,
                 quantile(ordered_qty, 0.01, na.rm = TRUE),
                 quantile(ordered_qty, 0.99, na.rm = TRUE))) %>% 
  ggplot(aes(ordered_qty)) +
  geom_histogram(fill = hue_pal()(2)[2], alpha = 0.6,
                 size = .25, color = "black") +
  labs(
    x = "Ordered quantity",
    y = "Number of order lines"
  ) +
  scale_x_continuous(labels = scales::label_number_si()) +
  scale_y_continuous(labels = scales::label_number_si()) +
   theme(text = element_text(size=6),
        plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
          ggsave(filename = "images/ordered_qty_1percent_linear.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

**log scale**
```{r}
{
order_line_qty_distinct %>% 
  filter(ordered_qty > 0) %>% 
  filter(between(ordered_qty,
                 quantile(ordered_qty, 0.01, na.rm = TRUE),
                 quantile(ordered_qty, 0.99, na.rm = TRUE))) %>% 
  ggplot(aes(ordered_qty)) +
  geom_histogram(fill = hue_pal()(2)[2], alpha = 0.6,
                 size = .25, color = "black") +
  labs(
    x = "Ordered quantity",
    y = "Number of order lines"
  ) +
  scale_x_continuous(
    trans = scales::log10_trans(),
    labels = scales::label_number_si(),
    breaks = 1:10) +
  scale_y_continuous(labels = scales::label_number_si()) +
   theme(text = element_text(size=6),
        plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
          ggsave(filename = "images/ordered_qty_1percent_log.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

# Sales Channels
```{r}
dat %>% 
  summarise(n_distinct(sales_channel))
```
Is there only one sales channel by order?

```{r}
dat %>% 
  select(order_num, sales_channel) %>% 
  distinct() -> sales_channel_by_order
```
Sales channel is not by order, it's by invoice.

```{r}
dat %>% 
  select(invoice_num, sales_channel) %>% 
  distinct() -> sales_channel_by_invoice

# sanity check
nrow(sales_channel_by_invoice) == summarise(dat, n_distinct(invoice_num))
```

Check for the most common sales channels
```{r}
sales_channel_by_invoice %>%
  count(sales_channel) -> sales_channel_count_by_invoice
```


# Intercompany

Check by row count
```{r}
dat %>% 
  count(intercompany)
```

Check by order count
```{r}
dat %>% 
  select(order_num, intercompany) %>% 
  distinct() -> intercompany_by_order
```

One order can be both intercompany and non-intercompany??
```{r}
dat %>%
  filter(order_num == 725393) %>% glimpse
```

# VIP and NON-vip

I'll try to find out same items for both vip and non-vip users
and compare the prices
```{r}
vip_items <- dat %>% 
  filter(top_customer_group == "STAR") %>% 
  select(top_customer_group, item_code) %>% 
  distinct()

nonvip_items <- dat %>% 
  filter(top_customer_group == "OTHER") %>% 
  select(top_customer_group, item_code) %>% 
  distinct()

```

VIP items: 3709
non-VIP items: 60046
- - - - - - - - - -
total items: 63020

There are obviously overlapping items.

```{r}
bind_rows(vip_items, nonvip_items) %>% 
  count(item_code) %>% 
  filter(n > 1) %>% 
  pull(item_code) -> overlapping_items
```

## Compare for overlapping items
```{r}
dat %>% 
  filter(item_code %in% overlapping_items) %>% 
  group_by(item_code, top_customer_group) %>% 
  summarise(avg_shipped = mean(invoiced_qty_shipped, na.rm = TRUE),
            invoiced_price = mean(invoiced_price, na.rm = TRUE)) ->
compare_overlapping

compare_overlapping %>% 
  ggplot(aes(top_customer_group, avg_shipped)) +
  geom_boxplot() +
  scale_y_log10()

compare_overlapping %>% 
  ggplot(aes(top_customer_group, invoiced_price)) +
  geom_boxplot() +
  scale_y_log10()
```

On dataset level for all items
```{r}
dat %>% 
  filter(invoiced_price > 0) %>% 
  select(top_customer_group, order_line_num, item_code, ordered_qty,
         invoiced_price) %>% 
  distinct() -> all_items_top_customer_group

all_items_top_customer_group %>% 
  filter(between(invoiced_price, quantile(invoiced_price, 0.01, na.rm = TRUE),
                 quantile(invoiced_price, 0.99, na.rm = TRUE))) %>% 
  ggplot(aes(top_customer_group, invoiced_price, fill = top_customer_group)) +
  geom_boxplot(show.legend = FALSE) +
  scale_y_log10(labels = scales::label_number_si()) +
  labs(
    x = "Customer groups",
    y = "Invoiced price"
  ) 

all_items_top_customer_group %>% 
  filter(between(ordered_qty, quantile(ordered_qty, 0.01, na.rm = TRUE),
                 quantile(ordered_qty, 0.99, na.rm = TRUE))) %>% 
  ggplot(aes(top_customer_group, ordered_qty, fill = top_customer_group)) +
  geom_boxplot(show.legend = FALSE) +
  scale_y_log10(labels = scales::label_number_si()) +
  labs(
    x = "Customer groups",
    y = "Ordered Quantity"
  ) 
```


## Example of overlapping item 1002285
This items has one STAR customer and another OTHER customer.
```{r}
dat %>%
  filter(item_code == "1002285") %>% 
  ggplot(aes(invoiced_price, cost_of_part, color = top_customer_group)) +
  geom_point(aes(size = invoiced_qty_shipped), alpha = 0.5) +
  xlim(0, 0.5) +
  ylim(0, 0.1)
```






