---
title: "EDA Part IV"
author: "Josip Domazet"
date: "5/11/2021"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Price discrimination

I need items which appeared in all customer regions
```{r}
dat %>% 
  filter(between(gm, 0, 1)) %>% 
  group_by(item_code, customer_region) %>% 
  summarise(n_customers = n_distinct(customer_id),
            n_manufacturing = n_distinct(manufacturing_region)) ->
  items_by_n_cr


# North America and Asia
items_by_n_cr %>% 
  group_by(item_code) %>% 
  summarise(america = sum(customer_region == "North America"),
            asia = sum(customer_region == "Asia"),
            europe = sum(customer_region == "Europe")) %>% 
  filter(america >= 1 & asia >= 1) -> items_cr_america_asia

dat %>% 
  filter(between(gm, 0, 1)) %>% 
  filter(cost_of_part > 0) %>% 
  
  # item produced in North America, 
  # but bought in all tree customer regions
  # 330-0022, 414348
  
  ```

## items with Cost of part equal to zero and positive
```{r}
dat %>% 
  group_by(item_code) %>% 
  summarise(zero = sum(cost_of_part == 0),
            positive = sum(cost_of_part > 0),
            n = n()) -> items_cost_0_positive
```


## gm == 1.00 

```{r}
dat %>% 
  filter(gm == 1.00) %>% 
  count(item_code, sort= T) %>% 
  count(manufacturing_region, sort = TRUE)
```

## Intercompany
```{r}
dat %>% 
  group_by(item_code) %>% 
  summarise(yes_intercompany= sum(intercompany == "YES", na.rm = TRUE),
            no_intercompany= sum(intercompany == "NO", na.rm = TRUE),
            n_orders = n_distinct(order_num)) %>% 
  filter(yes_intercompany >= 1 & no_intercompany >= 1) ->
  items_yes_no_intercompany

dat %>% 
  filter(item_code %in% items_yes_no_intercompany$item_code) %>% 
  filter_var_percent(invoiced_price, 0.01) %>% 
  filter(invoiced_qty_shipped > 0) %>% 
  filter(invoiced_price > 0) %>%  # zasto se ovo dogada?
  group_by(item_code, intercompany) %>% 
  summarise(price = median(invoiced_price, na.rm = TRUE),
            ordered_qty = median(ordered_qty, na.rm = TRUE),
            cost_of_part = median(cost_of_part, na.rm = TRUE),
            gm = median(gm, na.rm = TRUE)) %>% 
  ungroup() ->
  intercompany_items_price

{
  intercompany_items_price %>%
    #filter(cost_of_part > 0) %>% 
    filter(gm > 0 & gm < 1) %>% 
    filter_var_percent(gm, 0.001) %>% 
    ggplot(aes(intercompany, gm, group = intercompany)) + 
    geom_boxplot(aes(fill = intercompany), show.legend = FALSE) + 
    labs(
      x = "Intercompany",
      y = "Gross margin"
    ) +
    theme(text = element_text(size=6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
  ggsave(filename = "images/intercompany_gm.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)


```
Percent change is sometimes negative not because of intercompany,
it's because of economy of scale (cost of part decreases when
quantity is increased)
```{r}
{
  intercompany_items_price %>%
    #filter(cost_of_part > 0) %>% 
    filter_var_percent(gm, 0.001) %>% 
    ggplot(aes(intercompany, gm, group = intercompany)) + 
    geom_boxplot(aes(fill = intercompany), show.legend = FALSE) + 
    labs(
      x = "Intercompany",
      y = "Gross margin"
    ) +
    theme(text = element_text(size=6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
  ggsave(filename = "images/intercompany_gm.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)

```
For price
```{r}
{
  intercompany_items_price_clean <-
    intercompany_items_price %>% 
    group_by(item_code) %>% 
    summarise(intercompany = n_distinct(intercompany)) %>% 
    filter(intercompany > 1)
  
  intercompany_items_price %>%
    filter(item_code %in% intercompany_items_price_clean$item_code)
  group_by(item_code) %>% 
    summarise(diff_price = (intercompany == "YES")*price -
                (intercompany == "NO")*price)
  
  
  intercompany_items_price %>%
    filter(item_code %in% intercompany_items_price_clean$item_code) %>% 
    group_by(item_code) %>% 
    filter(between(
      ordered_qty[intercompany == "YES"]/ordered_qty[intercompany == "NO"],
      1/3, 3)) %>% 
    summarise(diff_price = (price[intercompany == "YES"] -
                              price[intercompany == "NO"]) / price[intercompany == "NO"]) %>% 
    ungroup() %>% 
    summarise(median_diff_price = median(diff_price, na.rm = TRUE))
  
  #filter(cost_of_part > 0) %>% 
  filter_var_percent(gm, 0.05) %>% 
    ggplot(aes(ordered_qty, price, color = intercompany)) + 
    geom_point() +
    scale_x_log10() +
    facet_wrap(~ intercompany)
  labs(
    x = "Intercompany",
    y = "Gross margin"
  ) +
    theme(text = element_text(size=6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
  ggsave(filename = "images/intercompany_gm.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)

```
Intercompany - cherrypicking
```{r}
# 184678 OK 
# 180936 GREAT
# 309433 GREAT for effect of quantity discount
{
  dat %>% 
    filter(item_code == "180936") %>% 
    filter(invoiced_qty_shipped > 0) %>% 
    filter(top_customer_group != "STAR") %>% 
   # filter(gm > 0 & gm < 1) %>% 
    #group_by(intercompany) %>% 
    #summarise(invoiced_price = mean(invoiced_price, na.rm = TRUE)) %>% 
    ggplot(aes(invoice_date, invoiced_price)) +
    geom_point(aes(color = intercompany),
               alpha= 0.55, show.legend = TRUE) +
    geom_hline(dat=data.frame(yintercept = 0.357, intercompany = "NO"),
               aes(yintercept = yintercept, color = intercompany),
               linetype = 2, size = 0.7, show.legend = FALSE,
               color = "black") +
    geom_hline(dat=data.frame(yintercept = 0.136, intercompany = "YES"),
               aes(yintercept = yintercept, color = intercompany),
               linetype = 2, size = 0.7, show.legend = FALSE,
               color = "black") +
    labs(
      x = "Invoice date",
      y = "Invoiced price",
      title = "Item code 180936"
    ) +
    theme(legend.position = "bottom",
          text = element_text(size=6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm")) +
    guides(colour = guide_legend(override.aes = list(alpha = 1)))
  } %>% 
  ggsave(filename = "images/intercompany_lower_price_item.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)

```


*Economy of scale example*
```{r}
{
  dat %>% 
    filter_var_percent(invoiced_price, 0.025) %>% 
    filter_var_percent(cost_of_part, 0.025) %>% 
    filter_var_percent(ordered_qty, 0.025) %>% 
    filter(cost_of_part >= 0) %>% 
    select(product_family, product_group, order_line_num, ordered_qty, invoiced_price, cost_of_part) %>% 
    distinct() %>% 
    sample_frac(0.1) %>% 
    #group_by(product_group) %>% 
    ggplot(aes(ordered_qty, cost_of_part)) +
    geom_point(aes(alpha = product_family), color = hue_pal()(2)[2],
               show.legend = FALSE, size = 0.5) +
    facet_wrap(~ product_family, scale = "free") +
    scale_alpha_manual(values = c("PF000" = 0.6, "PF001" = 0.025, "PF002" = 0.05)) +
    labs(
      x = "Ordered quantity",
      y = "Cost of part"
    ) +
    theme(text = element_text(size=6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm")) +
    scale_x_continuous(label = scales::label_number_si())
} %>% 
  ggsave(filename = "images/economy_of_scale_by_pf.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```
*Economy of scale* - two items 
```{r}
dat %>% 
  filter(item_code %in% c("000871","CP30G01")) %>%
  #select(item_code, ordered_qty, invoiced_price, cost_of_part, gm) %>% 
  filter(invoiced_price > 0) %>% 
  ggplot(aes(ordered_qty, cost_of_part)) +
  geom_point(aes(color = customer_region)) + 
  facet_wrap(~ item_code, scale = "free")

```



TODO: number of unique products ~ profit
## num_unique_on_product

```{r}
dat %>% 
  filter(between(gm, 0, 1)) %>% 
  filter(cost_of_part > 0) %>% 
  filter(intercompany != "YES") 
```
60.3 % of initial data set remains

```{r}
dat %>% 
  filter(between(gm, 0, 1)) %>% 
  filter(cost_of_part > 0) %>% 
  filter(intercompany != "YES") %>%  
  filter(num_of_unique_products_on_a_quote == 3) %>% view("1 item")
```

```{r}
dat %>% 
  filter(between(gm, 0, 1)) %>% 
  filter(cost_of_part > 0) %>% 
  filter(intercompany != "YES") %>%  
  filter(num_of_unique_products_on_a_quote == 4) %>% view("1 item)")
```


```{r}
dat %>% 
  filter(between(gm, 0, 1)) %>% 
  filter(cost_of_part > 0) %>% 
  mutate(profit = invoiced_qty_shipped * (invoiced_price - cost_of_part)) %>% 
  filter_var_percent(profit, 0.01) %>% 
  sample_frac(0.1) %>% 
  filter(num_of_unique_products_on_a_quote > 0) %>% 
  ggplot(aes(num_of_unique_products_on_a_quote, profit)) +
  geom_point()
```

## cost of part zero

```{r}
dat %>% 
  group_by(item_code, product_family) %>% 
  summarise(has_zero = sum(cost_of_part == 0), has_pos = sum(cost_of_part > 0),
            has_neg = sum(cost_of_part < 0)) %>% 
  ungroup() -> items_by_cost_of_part
```

We have around 63k items
Around 9k items have exclusively cost_of_part = 0.
Around 44k items have cost_of_part only positive.
Around 7k items have both zero and positive.


```{r}
items_zero_and_positive_cost <- items_by_cost_of_part %>% 
  filter(has_pos > 0 & has_zero > 0) %>% pull(item_code)

dat %>% 
  filter(item_code %in% items_zero_and_positive_cost) %>% 
  view("WTF")
```

## AVPU
Let's omit star customers and intercompany transactions
```{r}
dat %>% 
  filter(intercompany != "YES" & top_customer_group == "OTHER") %>% 
  filter(cost_of_part > 0 ) %>%
  filter(between(gm, 0, 1)) %>% 
  filter(invoiced_qty_shipped > 0) %>% 
  mutate(revenue = gm * invoiced_price * invoiced_qty_shipped) %>% 
  group_by(customer_region) %>% 
  summarise(total_revenue = sum(revenue),
            arpu = total_revenue / n_distinct(customer_id),
            n_users = n_distinct(customer_id)) %>% 
  filter(!is.na(customer_region)) -> avpu_by_customer_region

{
  avpu_by_customer_region %>% 
    mutate(customer_region = fct_reorder(customer_region, arpu)) %>% 
    ggplot(aes(arpu, customer_region, fill = customer_region)) +
    geom_col(width = 0.5,
             show.legend = FALSE) +
    labs(
      x = "Average revenue per user (AVPU)",
      y = "Customer region"
    ) +
    theme(text = element_text(size=6),
          plot.margin=grid::unit(c(2, 2.2, 2, 2), "mm")) +
    scale_fill_manual(
      values = c("Europe" = hue_pal()(4)[1],
                 "Asia" = hue_pal()(4)[2],
                 "North America" = hue_pal()(4)[3],
                 "(Missing)" = hue_pal()(4)[4]
      ))
} %>% 
  ggsave(filename = "images/arpu_customer_region.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

Fill by customer industry
```{r}
dat %>% 
  filter(intercompany != "YES" & top_customer_group == "OTHER") %>% 
  filter(cost_of_part > 0 ) %>%
  filter(between(gm, 0, 1)) %>% 
  filter(invoiced_qty_shipped > 0) %>% 
  mutate(revenue = gm * invoiced_price * invoiced_qty_shipped) %>% 
  group_by(customer_region, customer_industry) %>% 
  filter_var_percent(revenue, 0.01) %>%
  summarise(total_revenue = sum(revenue),
            arpu = total_revenue / n_distinct(customer_id),
            n_users = n_distinct(customer_id)) %>% 
  mutate(arpu = arpu / sum(arpu)) %>% 
  filter(!is.na(customer_region)) -> avpu_by_customer_region_and_industry

{
  avpu_by_customer_region_and_industry %>% 
    mutate(customer_region = fct_reorder(customer_region, arpu)) %>% 
    mutate(customer_industry = factor(customer_industry,
                                      levels = sort(customer_industry))) %>% 
    ggplot(aes(customer_region, arpu, fill = customer_industry)) +
    geom_col(
      width = 0.5) +
    labs(
      y = "AVPU percentage",
      x = "Customer region"
    ) +
    scale_y_continuous(labels = scales::percent) +
    guides(fill = guide_legend(reverse = T, nrow = 2)) +
    theme(text = element_text(size=6),
          plot.margin=grid::unit(c(2, 2.2, 2, 2), "mm"),
          legend.position = "top",
          legend.text = element_text(size = 3),
          legend.title = element_text(size = 3),
          legend.key.height= unit(0.45, 'cm'),
          legend.key.width= unit(0.45, 'cm')) +
    labs(fill = "Customer industry")
}  %>% 
  ggsave(filename = "images/arpu_customer_region_and_industry.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

STAR customer by region
```{r}
{
  dat %>% 
    filter(top_customer_group == "STAR") %>% 
    group_by(customer_region) %>% 
    summarise(n = n_distinct(customer_id)) %>% 
    mutate(customer_region = fct_reorder(customer_region, n)) %>% 
    ggplot(aes(n, customer_region, fill = customer_region, color = customer_region)) +
    geom_segment(aes(yend = customer_region, xend = 0),
                 show.legend = FALSE) +
    geom_point(size = 2, show.legend = FALSE) +
    scale_fill_manual(
      values = c("Europe" = hue_pal()(4)[1],
                 "Asia" = hue_pal()(4)[2],
                 "North America" = hue_pal()(4)[3],
                 "(Missing)" = hue_pal()(4)[4]
      )) +
    scale_color_manual(
      values = c("Europe" = hue_pal()(4)[1],
                 "Asia" = hue_pal()(4)[2],
                 "North America" = hue_pal()(4)[3],
                 "(Missing)" = hue_pal()(4)[4]
      )) +
    labs(
      x = "Number of STAR customers",
      y = NULL 
    ) +
    theme(text = element_text(size=6),
          plot.margin = grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
    ggsave(filename = "images/star_by_region.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```
  
  
Compare star and non-star quantities
```{r}
{
  dat %>% 
  #  filter(top_customer_group == "STAR") %>% 
  filter(gm > 0 & gm < 1) %>% 
  filter(invoiced_qty_shipped > 0) %>% 
  filter(ordered_qty > 0) %>% 
  filter_var_percent(ordered_qty, 0.001) %>% 
  #group_by(top_customer_group) %>% 
  #summarise(mean(ordered_qty, na.rm=T))
  ggplot(aes(top_customer_group, 
             ordered_qty, group = top_customer_group, fill = top_customer_group)) +
  geom_boxplot(show.legend = FALSE) +
  labs(
    x  = "Top customer group",
    y  = "Ordered Quantity"
  ) +
  scale_y_log10(labels = scales::label_number_si())  +
        theme(text = element_text(size=6),
          plot.margin = grid::unit(c(2, 0.3, 2, 2), "mm"))
  } %>% 
    ggsave(filename = "images/star_by_quantity.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

```{r}
{
  dat %>% 
  #  filter(top_customer_group == "STAR") %>% 
  filter(gm > 0 & gm < 1) %>% 
  filter(invoiced_qty_shipped > 0) %>% 
  filter(ordered_qty > 0) %>% 
  filter_var_percent(ordered_qty, 0.001) %>% 
  #group_by(top_customer_group) %>% 
  #summarise(mean(ordered_qty, na.rm=T))
  mutate(revenue = (invoiced_price - cost_of_part) * invoiced_qty_shipped) %>% 
  ggplot(aes(top_customer_group, 
             revenue, group = top_customer_group, fill = top_customer_group)) +
  geom_boxplot(show.legend = FALSE) +
  labs(
    x  = "Top customer group",
    y  = "Revenue of invoice line"
  ) +
  scale_y_log10(labels = scales::label_number_si())  +
        theme(text = element_text(size=6),
          plot.margin = grid::unit(c(2, 0.3, 2, 2), "mm"))
  } %>% 
    ggsave(filename = "images/star_by_revenue.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

  