---
title: "EDA - Part I"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---


## Packages
```{r}
library("tidyverse")
library("lubridate")
library("tidytext")
library("scales")
library("ggridges")
library("ggrepel")
theme_set(theme_bw())

clean <- function(tbl) {
  tbl %>% filter(cost_of_part > 0 &
                   invoiced_price > 0 &
                   gm <= 1 &
                   ordered_qty > 0 &
                   invoiced_qty_shipped > 0) 
  
}
```

## Data loading
```{r}

dat <- read.csv("./data/LUMEN_DS_corrected.csv",
                header= TRUE,
                stringsAsFactors = FALSE,
                sep = "|",
                quote = "\"",
                encoding = "UCS-2LE",
                fileEncoding =  "UCS-2LE",
                colClasses = "character") 

colnames(dat) <- c("manufacturing_region", "manufacturing_location_code",
                   "intercompany", "customer_id", "customer_industry",
                   "customer_region", "customer_first_invoice_date",
                   "top_customer_group", "item_code", "product_family",
                   "product_group", "price_last_modified_date_in_the_erp",
                   "born_on_date", "make_vs_buy", "sales_channel_internal",
                   "sales_channel_external", "sales_channel_grouping",
                   "invoice_date", "invoice_num", "invoice_line_num",
                   "order_date", "order_num", "order_line_num",
                   "invoiced_qty_shipped", "ordered_qty", "invoiced_price",
                   "invoiced_price_tx", "cost_of_part",
                   "material_cost_of_part", "labor_cost_of_part", 
                   "overhead_cost_of_part", "gm",
                   "num_of_unique_products_on_a_quote")

factor_colnames <- c("manufacturing_region",
                     "manufacturing_location_code",
                     "intercompany",
                     "customer_id",
                     "customer_industry",
                     "customer_region",
                     "top_customer_group",
                     "item_code",
                     "product_family",
                     "product_group",
                     "make_vs_buy",
                     "sales_channel_internal",
                     "sales_channel_external",
                     "sales_channel_grouping",
                     "invoice_num",
                     "invoice_line_num",
                     "order_num",
                     "order_line_num")

datetime_colnames <- c("price_last_modified_date_in_the_erp",
                       "customer_first_invoice_date")

date_colnames <- c("born_on_date",
                   "invoice_date",
                   "order_date")

numeric_colnames <- colnames(dat)[!colnames(dat) %in% c(factor_colnames,
                                                        datetime_colnames,
                                                        date_colnames)]

dat <- dat %>% 
  mutate(across(everything(), ~na_if(., "NaN"))) %>%  
  mutate(across(everything(),  ~na_if(., ""))) %>%
  mutate(across(all_of(factor_colnames), as.factor),
         across(all_of(numeric_colnames), as.numeric),
         across(all_of(datetime_colnames), lubridate::date),
         across(all_of(date_colnames), lubridate::ymd))

# remove some columns
dat <- dat %>% 
  rename(sales_channel = sales_channel_internal) %>% 
  select(c(-sales_channel_grouping, -sales_channel_external, -invoiced_price_tx))
```

The data is now loaded

## Counting things

First thing to do is to check how many unique users, items, man. regions, man. locations do we have

```{r}
dat %>% 
  summarise(across(all_of(factor_colnames), ~ n_distinct(.))) %>% 
  view("count distinct")
```

We have:
- around 12k users
- around 63k items
- around 780k orders
- around 1m invoices
- 3 manufacturing regions
- 31 manufacturing locations
- 15 customer industries
- 3 customer regions 
- 3 product families
- 32 product groups

```{r}
dat %>% 
  slice_sample(prop = 0.01) %>% 
  group_by(invoice_num) %>% 
  summarise(n_orders = n_distinct(order_num)) %>%
  view("Check are there invoices with multiple orders")
```

It turns out we have invoices with multiple orders.

```{r}
invoice_line_nums <- dat %>% pull(invoice_line_num)

tabl <- data.frame(table(invoice_line_nums))
tabl <- tabl %>% tibble()

sus <- tabl %>% filter(Freq > 1) %>% pull(invoice_line_nums)

dat_sus <- dat %>% filter(invoice_line_num %in% sus) 
```

### Manufacturing region
```{r}
plot_one_factor(dat, manufacturing_region) +
  labs(
    x = "Num. of rows",
    y = "Manufacturing region",
    title = "There are three known manufacturing regions"
  ) 
```



### Manufacturing location code
```{r}
plot_one_factor(dat, manufacturing_location_code)
```

Now plot inside manufacturing region
```{r}
plot_outer_inner_factor(dat, manufacturing_region, manufacturing_location_code) +
  labs(
    x = "Num. of rows",
    y = "Manufacturing location code",
    title = "Manufacturing location codes by manufacturing regions"
  ) -> man_loc_by_reg
```

### Customer industry
```{r}
plot_one_factor(dat, customer_industry) +
  labs(
    x = "Num. of rows",
    y = "Customer Industry",
    title = "Industry IC000 has the most rows in dataset"
  )
```

### Customer region
```{r}
### Manufacturing region
plot_one_factor(dat, customer_region) +
  labs(
    x = "Num. of rows",
    y = "Customer region",
    title = "There are three known manufacturing regions"
  ) 
```



### Which users are most frequent? 

```{r}
n_orders_by_customer <- dat %>% 
  group_by(customer_id, top_customer_group) %>% 
  summarise(n_orders = n_distinct(order_num)) %>% 
  ungroup()

n_orders_by_customer %>% 
  slice_max(n_orders, n = 100) %>% 
  mutate(customer_id = fct_reorder(customer_id, n_orders)) %>% 
  ggplot(aes(n_orders, customer_id, fill = top_customer_group)) +
  geom_col() +
  labs(
    x = "Num. of orders",
    y = "Customer ID"
  ) + 
  theme(axis.text.y = element_text(size = 5))
```

## Which users have multiple industries?
```{r}
n_industries_by_customer <- dat %>% 
  group_by(customer_id, top_customer_group) %>% 
  summarise(n_industries = n_distinct(customer_industry))

```



## Correlations
### Gross margin by customer industry
```{r}
dat %>% 
  group_by(customer_industry, top_customer_group) %>% 
  filter(between(gm, 
                 quantile(gm, 0.05, na.rm =TRUE),
                 quantile(gm, 0.95, na.rm = TRUE)
  )
  ) %>% 
  ungroup() %>% 
  mutate(customer_industry = fct_reorder(customer_industry, gm)) %>% 
  ggplot(aes(x = customer_industry, gm, fill = top_customer_group)) +
  geom_boxplot() + 
  labs(
    x = "Customer industry",
    y = "Gross margin",
    title = "Gross margin by customer industry",
    subtitle = "Industry IC012 has highest median of gross margin"
  ) + 
  theme(legend.position = "bottom")

```

#Product group
```{r}
plot_one_factor(dat, product_group)  +
  labs(
    x = "num. of rows",
    y = "Product groups",
    title = "Product group PC010 is in the highest number of rows",
    subtitle = "There are also many missing values (2nd highest value)"
  )
```


```{r}
dat %>% 
  filter(between(gm, 
                 quantile(gm, 0.05, na.rm =TRUE),
                 quantile(gm, 0.95, na.rm = TRUE)
  )
  ) %>% 
  ungroup() %>% 
  ggplot(aes(x = product_group, gm)) +
  geom_boxplot()


```

## Cost components
```{r}
dat %>% 
  select(gm, material_cost_of_part, labor_cost_of_part, overhead_cost_of_part) %>% 
  pivot_longer(cols = c(ends_with("cost_of_part")), 
               names_to = "cost_type",
               values_to = "value"
  ) %>% 
  filter(between(gm, quantile(gm, 0.05, na.rm = TRUE), quantile(gm, 0.95, na.rm = TRUE))) %>% 
  ggplot(aes(gm, value, fill = cost_type, color = cost_type)) +
  geom_hex(alpha = 0.8) +
  facet_wrap(~cost_type, scale = "free")
```

## Manufacturing regions <> Customer region
```{r}
dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  group_by(manufacturing_region, customer_region) %>% 
  tally() %>% 
  ungroup() %>% 
  view("Manufacturing region - customer region")
```

### Correlations between price components

```{r}
dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  group_by(manufacturing_region, 
           customer_region,
           top_customer_group,
           item_code) %>% 
  filter(n() >= 100) %>% 
  summarise(invoice_price_gm = cor(invoiced_price, gm, method = "spearman"),
            invoice_price_cost_of_part = cor(invoiced_price, cost_of_part, method = "spearman"),
            cost_of_part_gm = cor(cost_of_part, gm, method = "spearman")
  ) %>% 
  pivot_longer(cols = c(invoice_price_gm,
                        invoice_price_cost_of_part,
                        cost_of_part_gm
  )) %>% 
  mutate(name = fct_reorder(name, -value)) %>% 
  ggplot(aes(value, name, group = name)) +
  geom_density_ridges() +
  theme_grey()

# geom_boxplot() +
# scale_x_discrete(labels = c("cost_of_part ~ gm",
#                             "invoice_price ~ cost_of_part",
#                             "invoice_price ~ gm")) +
# labs(
#   x = "Variable combination", 
#   y = "Spearman correlation",
#   title = "Spearman correlation for pairs of variables",
#   subtitle = "After grouping by man. region, customer region,
#   customer group and item code"
# )

```


## Correlation between product groups

```{r}

means <-
  dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  filter(customer_region == manufacturing_region) %>% 
  filter(between(gm, quantile(gm, 0.05, na.rm = TRUE),
                 quantile(gm, 0.95, na.rm = TRUE))) %>% 
  group_by(customer_region) %>% 
  summarise(gm = mean(gm, na.rm = TRUE))

dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  filter(customer_region == manufacturing_region) %>% 
  filter(between(gm, quantile(gm, 0.05, na.rm = TRUE),
                 quantile(gm, 0.95, na.rm = TRUE))) %>% 
  mutate(customer_region = fct_reorder(customer_region, -gm, mean)) %>% 
  group_by(customer_region, top_customer_group, product_group) %>% 
  ggplot(aes(top_customer_group, gm, fill = product_group)) +
  geom_boxplot(alpha = 0.25) +
  facet_wrap(~customer_region, ncol = 1) +
  geom_hline(data = means, aes(yintercept = gm), size = 1,
             linetype = 2,
             color = "#EA060A") 


```

## 

```{r}
dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  filter(customer_region == "Europe") %>% 
  filter(item_code != "TRANSPORTKOSTEN") %>% 
  mutate(item_code = fct_lump_n(item_code, 10, w = invoiced_qty_shipped)) %>% 
  filter(item_code != "Other") %>% 
  count(item_code, wt = invoiced_qty_shipped) %>% 
  mutate(item_code = fct_reorder(item_code, n)) %>% 
  ggplot(aes(n, item_code)) +
  geom_col() +
  labs(
    x = "Total invoiced qty shipped",
    y = "item code"
  ) +
  scale_x_continuous(labels = scales::comma)
```

## Extract top 10 items in Europe
```{r}

dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  filter(customer_region == "Europe") %>% 
  filter(item_code != "TRANSPORTKOSTEN") %>% 
  mutate(item_code = fct_lump_n(item_code, 10, w = invoiced_qty_shipped)) %>% 
  filter(item_code != "Other") %>% 
  count(item_code, wt = invoiced_qty_shipped) -> top_10_items_europe

```

Check for top 10 items
```{r}
dat %>% 
  clean() %>% 
  filter(customer_region == "Europe") %>% 
  filter(item_code %in% top_10_items_europe$item_code) %>% 
  ggplot(aes(invoice_date, invoiced_price, color = item_code)) +
  geom_point()
```


## Extract top 10 product groups in Europe

```{r}
dat %>% 
  clean() %>% 
  filter(customer_region == "Europe" &
            manufacturing_region == "Europe") %>% 
  filter(item_code != "TRANSPORTKOSTEN") %>% 
  mutate(product_group = fct_lump_n(product_group, 5, w = invoiced_qty_shipped)) %>% 
  filter(product_group != "Other") %>% 
  count(product_group, wt = invoiced_qty_shipped) -> top_product_groups_europe

```

```{r}
dat %>% 
  clean() %>% 
  filter(customer_region == "Europe" & 
           manufacturing_region == "Europe") %>% 
  mutate(product_group = fct_explicit_na(product_group)) %>% 
  mutate(product_group = fct_reorder(product_group, -invoiced_qty_shipped, function(x) sum(x, na.rm = TRUE))) %>% 
  ggplot(aes(invoice_date, invoiced_price, color = product_group)) +
  geom_point(alpha = 0.2, show.legend = FALSE) +
  scale_y_log10(labels = scales::comma) +
  facet_wrap(~product_group) +
  labs(
    x = "Invoice date",
    y = "Invoice price",
    title = "Europe's invoice price by product groups"
  )
```

## Dates analysis


### Born on date - median and mean
I'll calculate median and mean born_on_date, but also median and mean of invoiced_price and gm.
```{r}
dat %>% 
  clean() %>% 
  mutate(product_group = fct_explicit_na(product_group)) %>% 
  group_by(product_family, product_group) %>%
  summarise(across(c(born_on_date, invoiced_price, gm),
                   list(mean = ~ mean(., na.rm = TRUE),
                        median = ~ median(., na.rm = TRUE))
                   ),
            n = n()
            ) %>% 
  ungroup() %>% 
  ggplot(aes(born_on_date_median, gm_median, color = product_family)) +
  geom_point(aes(size = n)) +
  #geom_text_repel(aes(label = product_group), vjust = -1) +
  labs(
    x = "Median of born on date",
    y = "Median of gross margin",
    title = "Product groups with older median of born on date\n tend to have smaller median of gross margin"
  ) +
  scale_size_continuous(labels = scales::comma)
```

### Frequency of orders 

The idea is to find how often do user make orders.
```{r}
order_date_by_customer <-
  dat %>% 
  clean() %>% 
  group_by(customer_id, order_num) %>% 
  summarise(order_date = min(order_date)) %>% 
  filter(year(order_date) != 9999) %>% 
  ungroup() %>% 
  mutate(customer_id = fct_lump_n(customer_id, 25)) %>% 
  filter(customer_id != "Other") 
  
order_date_by_customer %>% 
  filter(year(order_date) >= 2017) %>% 
  #filter(customer_id != 19244) %>% 
  ggplot(aes(order_date, customer_id)) +
  geom_point()
```
