---
title: "EDA - Part I"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---


## Packages

The following packages are used in all of RMarkdown files.
```{r}
library("tidyverse")
library("lubridate")
library("tidytext")
library("scales")
library("ggridges")
library("ggrepel")
theme_set(theme_bw())
```

## Data set loading
```{r}
dat <- read.csv("./dataset/LUMEN_DS.csv",
                header= TRUE,
                stringsAsFactors = FALSE,
                sep = "|",
                quote = "\"",
                encoding = "UCS-2LE",
                fileEncoding =  "UCS-2LE",
                colClasses = "character") 

original_colnames <- c("manufacturing_region", "manufacturing_location_code",
                   "intercompany", "customer_id", "customer_industry",
                   "customer_region", "customer_first_invoice_date",
                   "top_customer_group", "item_code", "product_family",
                   "product_group", "price_last_modified_date_in_the_erp",
                   "born_on_date", "make_vs_buy", "sales_channel_internal",
                   "sales_channel_external", "sales_channel_grouping",
                   "invoice_date", "invoice_num", "invoice_line_num",
                   "order_date", "order_num", "order_line_num",
                   "invoiced_qty_shipped", "ordered_qty", "invoiced_price",
                   "invoiced_price_tx", "cost_of_part",
                   "material_cost_of_part", "labor_cost_of_part", 
                   "overhead_cost_of_part", "gm",
                   "num_of_unique_products_on_a_quote")

colnames(dat) <- c("manufacturing_region", "manufacturing_location_code",
                   "intercompany", "customer_id", "customer_industry",
                   "customer_region", "customer_first_invoice_date",
                   "top_customer_group", "item_code", "product_family",
                   "product_group", "price_last_modified_date_in_the_erp",
                   "born_on_date", "make_vs_buy", "sales_channel_internal",
                   "sales_channel_external", "sales_channel_grouping",
                   "invoice_date", "invoice_num", "invoice_line_num",
                   "order_date", "order_num", "order_line_num",
                   "invoiced_qty_shipped", "ordered_qty", "invoiced_price",
                   "invoiced_price_tx", "cost_of_part",
                   "material_cost_of_part", "labor_cost_of_part", 
                   "overhead_cost_of_part", "gm",
                   "num_of_unique_products_on_a_quote")

factor_colnames <- c("manufacturing_region",
                     "manufacturing_location_code",
                     "intercompany",
                     "customer_id",
                     "customer_industry",
                     "customer_region",
                     "top_customer_group",
                     "item_code",
                     "product_family",
                     "product_group",
                     "make_vs_buy",
                     "sales_channel_internal",
                     "sales_channel_external",
                     "sales_channel_grouping",
                     "sales_channel",
                     "invoice_num",
                     "invoice_line_num",
                     "order_num",
                     "order_line_num")

datetime_colnames <- c("price_last_modified_date_in_the_erp",
                       "customer_first_invoice_date")

date_colnames <- c("born_on_date",
                   "invoice_date",
                   "order_date")

numeric_colnames <- colnames(dat)[!colnames(dat) %in% c(factor_colnames,
                                                        datetime_colnames,
                                                        date_colnames)]

dat <- dat %>% 
  mutate(across(everything(), ~na_if(., "NaN"))) %>%  
  mutate(across(everything(),  ~na_if(., ""))) %>%
  mutate(across(all_of(factor_colnames), as.factor),
         across(all_of(numeric_colnames), as.numeric),
         across(all_of(datetime_colnames), lubridate::date),
         across(all_of(date_colnames), lubridate::ymd))

# remove some columns
dat <- dat %>% 
  rename(sales_channel = sales_channel_internal) %>% 
  select(c(-sales_channel_grouping, -sales_channel_external, -invoiced_price_tx))
```

The data is now loaded

## Counting things

First thing to do is to check how many unique users, items, man. regions, man. locations do we have

### Invoice - order columns
```{r}
{
  dat %>% 
  summarise(across(all_of(factor_colnames), ~ n_distinct(.))) %>% 
  pivot_longer(everything()) %>% 
  filter(name %in% c("order_num", "invoice_num", "invoice_line_num", "order_line_num")) %>% 
  mutate(name = fct_reorder(name, value)) %>% 
  ggplot(aes(value, name)) +
  geom_col() +
  labs(
    x = "Number of unique values",
    y = "Column name"
  ) +
  scale_x_continuous(labels = scales::comma, breaks = seq(0, 1300000, 250000),
                     minor_breaks = NULL) +
  theme(text = element_text(size=6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
  ggsave(filename = "..plots/invoice_order_columns_plot.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

### Customers by region
```{r}
{
  dat %>% 
  group_by(customer_region) %>% 
  summarise(n_customers = n_distinct(customer_id)) %>% 
  mutate(customer_region = fct_explicit_na(customer_region)) %>% 
  mutate(customer_region = fct_reorder(customer_region, n_customers)) %>% 
  ggplot(aes(n_customers, customer_region, fill = customer_region)) + 
  geom_col(width = 0.5, show.legend = FALSE) +
  labs(
    x = "Number of customers",
    y = "Customer region"
  ) +
  scale_fill_manual(
    values = c("Europe" = hue_pal()(4)[1],
               "Asia" = hue_pal()(4)[2],
               "North America" = hue_pal()(4)[3],
               "(Missing)" = hue_pal()(4)[4]
    )
  ) +
  theme(text = element_text(size=6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
  ggsave(filename = "..plots/customers_by_region.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

### Customers by region + top_customer_group
```{r}
{
  dat %>% 
  filter(top_customer_group == "STAR") %>% 
  group_by(customer_region) %>% 
  summarise(n_customers = n_distinct(customer_id)) %>% 
  ungroup() %>% 
  mutate(customer_region = fct_explicit_na(customer_region)) %>%
  mutate(customer_region = fct_expand(customer_region, "")) %>% 
  mutate(customer_region = fct_reorder(customer_region, n_customers)) %>% 
  ggplot(aes(n_customers, customer_region, fill = customer_region)) + 
  geom_col(width = 0.5, show.legend = FALSE) +
  labs(
    x = "Number of customers",
    y = "Customer region"
  ) +
   scale_fill_manual(
    values = c("Europe" = hue_pal()(4)[1],
               "Asia" = hue_pal()(4)[2],
               "North America" = hue_pal()(4)[3],
               "(Missing)" = hue_pal()(4)[4]
    )
  ) +
  theme(text = element_text(size = 6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
  ggsave(filename = "..plots/customers_by_region_star.pdf", 
         width = 5,
         height = 5,
         units = "cm",
         dpi = 250,
         device = pdf)

{
  dat %>% 
  filter(!is.na(customer_region)) %>% 
  filter(top_customer_group == "OTHER") %>% 
  group_by(customer_region) %>% 
  summarise(n_customers = n_distinct(customer_id)) %>% 
  ungroup() %>% 
  mutate(customer_region = fct_explicit_na(customer_region)) %>% 
  mutate(customer_region = fct_reorder(customer_region, n_customers)) %>% 
  ggplot(aes(n_customers, customer_region, fill = customer_region)) + 
  geom_col(width = 0.5, show.legend = FALSE) +
  labs(
    x = "Number of customers",
    y = "Customer region"
  ) +
   scale_fill_manual(
    values = c("Europe" = hue_pal()(4)[1],
               "Asia" = hue_pal()(4)[2],
               "North America" = hue_pal()(4)[3],
               "(Missing)" = hue_pal()(4)[4]
    )
  ) +
    theme(text = element_text(size = 6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
  ggsave(filename = "..plots/customers_by_region_other.pdf", 
         width = 5,
         height = 5,
         units = "cm",
         dpi = 250,
         device = pdf)
```

### Customers by customer industry
```{r}
customers_by_customer_industry_plot <-
  dat %>% 
  mutate(customer_industry = fct_explicit_na(customer_industry)) %>% 
  group_by(customer_industry) %>% 
  summarise(n_customers = n_distinct(customer_id)) %>% 
  mutate(customer_industry = fct_reorder(customer_industry, n_customers)) %>% 
  ggplot(aes(n_customers, customer_industry)) +
  #geom_segment(aes(yend = customer_industry, xend = 0)) +
  #geom_point(size = 4) +
  geom_col(fill = hue_pal()(2)[2], alpha = 0.6) +
  labs(
    x = "Number of customers",
    y = "Customer industry"
  )

customers_by_customer_industry_plot %>% 
  ggsave(filename = "..plots/customers_by_customer_industry.pdf", 
         width = 14,
         height = 14,
         units = "cm",
         dpi = 300,
         device = pdf)
```

### Customers segmented by first invoice date 
Raw histogram
```{r}
dat %>% 
  select(customer_id, customer_first_invoice_date) %>% 
  distinct() %>% 
  ggplot(aes(customer_first_invoice_date)) +
  geom_histogram() + 
  labs(
    x = "First invoice date",
    y = "Count"
  )

```

Trunc to year
```{r}
customer_first_invoice_by_year_plot <-
  dat %>% 
  select(customer_id, customer_first_invoice_date) %>% 
  distinct() %>% 
  mutate(customer_first_invoice_date = year(customer_first_invoice_date)) %>% 
  group_by(customer_first_invoice_date) %>% 
  summarise(n_customers = n_distinct(customer_id)) %>% 
  ggplot(aes(
    customer_first_invoice_date, 
    n_customers,
    fill = customer_first_invoice_date %in% 2015:2020)) +
  geom_col(show.legend = FALSE) +
  labs(
    x = "First invoice date",
    y = "Count"
  ) + 
  scale_x_continuous(breaks = seq(1990, 2020, 2)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
         text = element_text(size=6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))

customer_first_invoice_by_year_plot %>% 
  ggsave(filename = "..plots/customer_first_invoice_by_year.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

Cumsum (use arrange)
```{r}
dat %>% 
  select(customer_id, customer_first_invoice_date) %>% 
  distinct() %>% 
  mutate(customer_first_invoice_date = year(customer_first_invoice_date)) %>% 
  group_by(customer_first_invoice_date) %>% 
  summarise(n_customers = n_distinct(customer_id)) %>% 
  arrange(-customer_first_invoice_date) %>% 
  mutate(percent = n_customers / sum(n_customers)) %>% 
  mutate(percent_cumsum = cumsum(percent)) 
```


### Order item lines by manufacturing region
```{r}
  dat %>% 
  mutate(across(starts_with("manufacturing"), ~ fct_explicit_na(.))) %>% 
  group_by(manufacturing_region) %>% 
  tally() %>% 
  arrange(desc(n))
```

### Order item lines by manufacturing region and location
```{r}
n_order_lines_by_man_region_loc_plot <-
  dat %>% 
  mutate(across(starts_with("manufacturing"), ~ fct_explicit_na(.))) %>% 
  group_by(manufacturing_region, manufacturing_location_code) %>% 
 # summarise(n_lines = n_distinct(order_line_num)) %>%  
#  ungroup() %>% 
  tally() %>% 
  mutate(n_lines = n) %>% 
  mutate(manufacturing_region = fct_reorder(manufacturing_region,n_lines, sum)) %>% 
  mutate(manufacturing_location_code = reorder_within(manufacturing_location_code,
                                                      n_lines,
                                                      manufacturing_region)) %>% 
  ggplot(aes(n_lines, manufacturing_location_code, fill = manufacturing_region)) +
  geom_col() +
  scale_y_reordered() +
  facet_wrap(~ manufacturing_region, scales = "free_y", dir = "v") +
  guides(fill = FALSE) +
  labs(
    x = "Number of data set rows",
    y  = "Manufacturing location code"
  ) + 
  scale_fill_manual(
    values = c("Europe" = hue_pal()(4)[1],
               "Asia" = hue_pal()(4)[2],
               "North America" = hue_pal()(4)[3],
               "(Missing)" = hue_pal()(4)[4]
    )
  ) +
  scale_x_continuous(minor_breaks = NULL,  labels =  scales::label_number_si()) 

n_order_lines_by_man_region_loc_plot %>% 
  ggsave(filename = "..plots/n_order_lines_by_man_region_loc.pdf", 
         width = 11,
         height = 11,
         units = "cm",
         dpi = 300,
         device = pdf)
```

### Num. of distinct items by product group
```{r}
n_items_by_product_group_plot <-
  dat %>% 
  mutate(across(starts_with("product_"), ~ fct_explicit_na(.))) %>% 
  filter(product_family != "PF000") %>% 
  group_by(product_family, product_group) %>% 
  summarise(n_items = n_distinct(item_code)) %>%  
  ungroup() %>% 
  mutate(product_family = fct_reorder(product_family,-n_items, sum)) %>% 
  mutate(product_group = reorder_within(product_group,
                                                      n_items,
                                                      product_family)) %>% 
  ggplot(aes(n_items, product_group, fill = product_family)) +
  geom_col() +
  scale_y_reordered() +
  facet_wrap(~ product_family, scales = "free_y") +
  guides(fill = FALSE) +
  labs(
    x = "Number of unique items",
    y  = "Product group"
  ) +
  scale_x_continuous(minor_breaks = NULL,  labels =  scales::label_number_si()) 

n_items_by_product_group_plot %>% 
    ggsave(filename = "n_items_by_product_group.pdf", 
         width = 11,
         height = 11,
         units = "cm",
         dpi = 300,
         device = pdf)
```


We have:
- around 12k users
- around 63k items
- around 780k orders
- around 1m invoices
- 3 manufacturing regions
- 29 manufacturing locations
- 15 customer industries
- 3 customer regions 
- 3 product families
- 31 product groups

```{r}
dat %>% 
  slice_sample(prop = 0.01) %>% 
  group_by(invoice_num) %>% 
  summarise(n_orders = n_distinct(order_num)) %>%
  view("Check are there invoices with multiple orders")
```

It turns out we have invoices with multiple orders.

```{r}
invoice_line_nums <- dat %>% pull(invoice_line_num)

tabl <- data.frame(table(invoice_line_nums))
tabl <- tabl %>% tibble()

sus <- tabl %>% filter(Freq > 1) %>% pull(invoice_line_nums)

dat_sus <- dat %>% filter(invoice_line_num %in% sus) 
```

### Manufacturing region
```{r}
plot_one_factor(dat, manufacturing_region) +
  labs(
    x = "Num. of rows",
    y = "Manufacturing region",
    title = "There are three known manufacturing regions"
  ) 
```



### Manufacturing location code
```{r}
plot_one_factor(dat, manufacturing_location_code)
```

Now plot inside manufacturing region
```{r}
plot_outer_inner_factor(dat, manufacturing_region, manufacturing_location_code) +
  labs(
    x = "Num. of rows",
    y = "Manufacturing location code",
    title = "Manufacturing location codes by manufacturing regions"
  ) -> man_loc_by_reg
```

### Customer industry
```{r}
plot_one_factor(dat, customer_industry) +
  labs(
    x = "Num. of rows",
    y = "Customer Industry",
    title = "Industry IC000 has the most rows in dataset"
  )
```

### Customer region
```{r}
### Manufacturing region
plot_one_factor(dat, customer_region) +
  labs(
    x = "Num. of rows",
    y = "Customer region",
    title = "There are three known manufacturing regions"
  ) 
```



### Which users are most frequent? 

```{r}
n_orders_by_customer <- dat %>% 
  group_by(customer_id, top_customer_group) %>% 
  summarise(n_orders = n_distinct(order_num)) %>% 
  ungroup()

n_orders_by_customer %>% 
  slice_max(n_orders, n = 100) %>% 
  mutate(customer_id = fct_reorder(customer_id, n_orders)) %>% 
  ggplot(aes(n_orders, customer_id, fill = top_customer_group)) +
  geom_col() +
  labs(
    x = "Num. of orders",
    y = "Customer ID"
  ) + 
  theme(axis.text.y = element_text(size = 5))
```

## Which users have multiple industries?
```{r}
n_industries_by_customer <- dat %>% 
  group_by(customer_id, top_customer_group) %>% 
  summarise(n_industries = n_distinct(customer_industry))

```



## Correlations
### Gross margin by customer industry
```{r}
dat %>% 
  group_by(customer_industry, top_customer_group) %>% 
  filter(between(gm, 
                 quantile(gm, 0.05, na.rm =TRUE),
                 quantile(gm, 0.95, na.rm = TRUE)
  )
  ) %>% 
  ungroup() %>% 
  mutate(customer_industry = fct_reorder(customer_industry, gm)) %>% 
  ggplot(aes(x = customer_industry, gm, fill = top_customer_group)) +
  geom_boxplot() + 
  labs(
    x = "Customer industry",
    y = "Gross margin",
    title = "Gross margin by customer industry",
    subtitle = "Industry IC012 has highest median of gross margin"
  ) + 
  theme(legend.position = "bottom")

```

#Product group
```{r}
plot_one_factor(dat, product_group)  +
  labs(
    x = "num. of rows",
    y = "Product groups",
    title = "Product group PC010 is in the highest number of rows",
    subtitle = "There are also many missing values (2nd highest value)"
  )
```


```{r}
dat %>% 
  filter(between(gm, 
                 quantile(gm, 0.05, na.rm =TRUE),
                 quantile(gm, 0.95, na.rm = TRUE)
  )
  ) %>% 
  ungroup() %>% 
  ggplot(aes(x = product_group, gm)) +
  geom_boxplot()


```

## Cost components
```{r}
dat %>% 
  select(gm, material_cost_of_part, labor_cost_of_part, overhead_cost_of_part) %>% 
  pivot_longer(cols = c(ends_with("cost_of_part")), 
               names_to = "cost_type",
               values_to = "value"
  ) %>% 
  filter(between(gm, quantile(gm, 0.05, na.rm = TRUE), quantile(gm, 0.95, na.rm = TRUE))) %>% 
  ggplot(aes(gm, value, fill = cost_type, color = cost_type)) +
  geom_hex(alpha = 0.8) +
  facet_wrap(~cost_type, scale = "free")
```

## Manufacturing regions <> Customer region
```{r}
dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  group_by(manufacturing_region, customer_region) %>% 
  tally() %>% 
  ungroup() %>% 
  view("Manufacturing region - customer region")
```

### Correlations between price components

```{r}
dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  group_by(manufacturing_region, 
           customer_region,
           top_customer_group,
           item_code) %>% 
  filter(n() >= 100) %>% 
  summarise(invoice_price_gm = cor(invoiced_price, gm, method = "spearman"),
            invoice_price_cost_of_part = cor(invoiced_price, cost_of_part, method = "spearman"),
            cost_of_part_gm = cor(cost_of_part, gm, method = "spearman")
  ) %>% 
  pivot_longer(cols = c(invoice_price_gm,
                        invoice_price_cost_of_part,
                        cost_of_part_gm
  )) %>% 
  mutate(name = fct_reorder(name, -value)) %>% 
  ggplot(aes(value, name, group = name)) +
  geom_density_ridges() +
  theme_grey()

# geom_boxplot() +
# scale_x_discrete(labels = c("cost_of_part ~ gm",
#                             "invoice_price ~ cost_of_part",
#                             "invoice_price ~ gm")) +
# labs(
#   x = "Variable combination", 
#   y = "Spearman correlation",
#   title = "Spearman correlation for pairs of variables",
#   subtitle = "After grouping by man. region, customer region,
#   customer group and item code"
# )

```


## Correlation between product groups

```{r}

means <-
  dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  filter(customer_region == manufacturing_region) %>% 
  filter(between(gm, quantile(gm, 0.05, na.rm = TRUE),
                 quantile(gm, 0.95, na.rm = TRUE))) %>% 
  group_by(customer_region) %>% 
  summarise(gm = mean(gm, na.rm = TRUE))

dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  filter(customer_region == manufacturing_region) %>% 
  filter(between(gm, quantile(gm, 0.05, na.rm = TRUE),
                 quantile(gm, 0.95, na.rm = TRUE))) %>% 
  mutate(customer_region = fct_reorder(customer_region, -gm, mean)) %>% 
  group_by(customer_region, top_customer_group, product_group) %>% 
  ggplot(aes(top_customer_group, gm, fill = product_group)) +
  geom_boxplot(alpha = 0.25) +
  facet_wrap(~customer_region, ncol = 1) +
  geom_hline(data = means, aes(yintercept = gm), size = 1,
             linetype = 2,
             color = "#EA060A") 


```

## 

```{r}
dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  filter(customer_region == "Europe") %>% 
  filter(item_code != "TRANSPORTKOSTEN") %>% 
  mutate(item_code = fct_lump_n(item_code, 10, w = invoiced_qty_shipped)) %>% 
  filter(item_code != "Other") %>% 
  count(item_code, wt = invoiced_qty_shipped) %>% 
  mutate(item_code = fct_reorder(item_code, n)) %>% 
  ggplot(aes(n, item_code)) +
  geom_col() +
  labs(
    x = "Total invoiced qty shipped",
    y = "item code"
  ) +
  scale_x_continuous(labels = scales::comma)
```

## Extract top 10 items in Europe
```{r}

dat %>% 
  filter(cost_of_part > 0 &
           invoiced_price > 0 &
           gm <= 1 &
           ordered_qty > 0 &
           invoiced_qty_shipped > 0) %>% 
  filter(customer_region == "Europe") %>% 
  filter(item_code != "TRANSPORTKOSTEN") %>% 
  mutate(item_code = fct_lump_n(item_code, 10, w = invoiced_qty_shipped)) %>% 
  filter(item_code != "Other") %>% 
  count(item_code, wt = invoiced_qty_shipped) -> top_10_items_europe

```

Check for top 10 items
```{r}
dat %>% 
  clean() %>% 
  filter(customer_region == "Europe") %>% 
  filter(item_code %in% top_10_items_europe$item_code) %>% 
  ggplot(aes(invoice_date, invoiced_price, color = item_code)) +
  geom_point()
```


## Extract top 10 product groups in Europe

```{r}
dat %>% 
  clean() %>% 
  filter(customer_region == "Europe" &
            manufacturing_region == "Europe") %>% 
  filter(item_code != "TRANSPORTKOSTEN") %>% 
  mutate(product_group = fct_lump_n(product_group, 5, w = invoiced_qty_shipped)) %>% 
  filter(product_group != "Other") %>% 
  count(product_group, wt = invoiced_qty_shipped) -> top_product_groups_europe

```

```{r}
dat %>% 
  clean() %>% 
  filter(customer_region == "Europe" & 
           manufacturing_region == "Europe") %>% 
  mutate(product_group = fct_explicit_na(product_group)) %>% 
  mutate(product_group = fct_reorder(product_group, -invoiced_qty_shipped, function(x) sum(x, na.rm = TRUE))) %>% 
  ggplot(aes(invoice_date, invoiced_price, color = product_group)) +
  geom_point(alpha = 0.2, show.legend = FALSE) +
  scale_y_log10(labels = scales::comma) +
  facet_wrap(~product_group) +
  labs(
    x = "Invoice date",
    y = "Invoice price",
    title = "Europe's invoice price by product groups"
  )
```

## Dates analysis


### Born on date - median and mean
I'll calculate median and mean born_on_date, but also median and mean of invoiced_price and gm.
```{r}
dat %>% 
  clean() %>% 
  mutate(product_group = fct_explicit_na(product_group)) %>% 
  group_by(product_family, product_group) %>%
  summarise(across(c(born_on_date,
                     invoiced_price, 
                     
                     gm),
                   list(mean = ~ mean(., na.rm = TRUE),
                        median = ~ median(., na.rm = TRUE))
                   ),
            n = n()
            ) %>% 
  ungroup() %>% 
  ggplot(aes(born_on_date_median, gm_median, color = product_family)) +
  geom_point(aes(size = n)) +
  #geom_text_repel(aes(label = product_group), vjust = -1) +
  labs(
    x = "Median of born on date",
    y = "Median of gross margin",
    title = "Product groups with older median of born on date\n tend to have smaller median of gross margin"
  ) +
  scale_size_continuous(labels = scales::comma) +
  guides(size = FALSE)
```


### Calculating average difference in order dates

The idea is to find how often do user make orders.

First I'll group by customer *and* order.
For each _order_ (**order_num**), I'll extract:
- order date (**already on  order level**)
- number of unique products (**already on order level**)
- total order price
- total quantity 
- average unit cost price
- average invoiced price
- average gross margin 
- most frequent product group (questionable)


```{r}
order_date_by_customer <-
  dat %>% 
  clean() %>% 
  filter(year(order_date) != 9999) %>% # junk in data
  group_by(customer_id, 
           customer_industry,
           customer_region,
           top_customer_group,
           order_num
           ) %>% 
  summarise(order_date = min(order_date),
            total_price = sum(invoiced_price * invoiced_qty_shipped,
                              na.rm = TRUE),
            total_qty = sum(invoiced_qty_shipped, na.rm = TRUE),
            mean_cost_of_part = mean(cost_of_part, na.rm = TRUE),
            mean_invoice_price = mean(invoiced_price, na.rm = TRUE),
            n_products = min(num_of_unique_products_on_a_quote, na.rm = TRUE),
            mean_gm = mean(gm, na.rm = TRUE),
            product_group = names(which.max(table(product_group)))
            ) %>% 
  ungroup()  
```


Now I'll aggregate data only by customer.
For each customer we'll know:
- what was avg. difference between two orders
- total number of orders
- average gross margin 
- average total price of orders
- average cost of part for orders
- average number of unique products on orders
- the date of first order
- the date of last order
- most frequent product group
```{r}
order_date_by_customer %>% 
  arrange(order_date) %>% 
  group_by(customer_id,
         customer_industry,
         customer_region,
         top_customer_group) %>% 
  # data is already grouped by customer and order
  summarise(avg_diff = sum(difftime(order_date, 
                                    lag(order_date), 
                                    units = "days"
                                    ),
                           na.rm = TRUE
                           ) / (n_distinct(order_date) - 1),
            n_orders = n_distinct(order_num),
            mean_gm = mean(mean_gm, na.rm = TRUE),
            mean_total_price = mean(total_price, na.rm = TRUE),
            total_price = sum(total_price),
            mean_total_qty = mean(total_qty, na.rm = TRUE),
            total_qty = sum(total_qty, na.rm = TRUE),
            mean_cost_of_part = mean(mean_cost_of_part, na.rm = TRUE),
            mean_n_product = mean(n_products, na.rm = TRUE),
            min_order_date = min(order_date, na.rm = TRUE),
            max_order_date = max(order_date, na.rm = TRUE),
            product_group = names(which.max(table(product_group)))
            ) %>% 
  mutate(avg_diff = as.numeric(avg_diff)) %>% 
  ungroup() -> avg_diff_order_date_customers

```
 
###Histogram of average diff for order date
```{r}
avg_diff_order_date_customers %>% 
  filter(!is.na(avg_diff) & avg_diff > 0) %>% 
  filter(n_orders > 0) %>% 
  ggplot(aes(avg_diff)) +
  geom_density_ridges(stat = "binline",
                      bins = 15,
                      aes(y = customer_region, fill = customer_region),
                      alpha = 0.9) +
  #geom_histogram(aes(fill = customer_region), alpha = 0.5) +
  scale_x_log10(labels = scales::comma) +
  labs(
    title = "Average difference of two consecutive orders by customer regions",
    x = "Num. of days",
    y = "Customer region"
  ) +
  theme(legend.position = "none") +
  facet_wrap(~ customer_industry, nrow = 5)
```


###Check correlation of mean cost of part (how expensive parts do  customers order) and mean total quantity 
```{r}
avg_diff_order_date_customers %>% 
  filter(!is.na(customer_region)) %>% 
  #filter_percent(mean_gm, 0.2) %>% 
  ggplot(aes(mean_total_qty, mean_cost_of_part)) +
  geom_point(aes(color = customer_region), alpha = 0.5) + 
  scale_y_log10(labels = scales::comma) +
  scale_x_log10(labels = scales::comma) +
  facet_wrap(~ customer_region) +
  guides(color = FALSE) +
  labs(
    x = "mean total quantity",
    y = "mean cost of part",
    title = NULL
  ) 
```

###Check correlation of customer_industry and gross margin
```{r}
avg_diff_order_date_customers %>% 
  filter(!is.na(customer_industry)) %>% 
  filter_percent(mean_gm, 0.05) %>% 
  mutate(customer_industry = fct_reorder(customer_industry, mean_gm)) %>% 
  ggplot(aes(customer_industry, mean_gm, 
             fill = customer_industry %in% c("IC007", "IC008", "IC000"))) +
  geom_boxplot() + 
  scale_fill_manual(name = "Is in top 3?",
                      labels = c("No", "Yes"),
                      values = hue_pal()(2)
                      )
  
```

###Check correlation of customer industry and cost of part
```{r}
avg_diff_order_date_customers %>% 
  filter(!is.na(customer_industry)) %>% 
  filter_percent(mean_cost_of_part, 0.1) %>% 
  mutate(customer_industry = fct_reorder(customer_industry, mean_cost_of_part)) %>% 
  ggplot(aes(customer_industry, mean_cost_of_part, 
             fill = customer_industry %in% c("IC007", "IC008", "IC000"))) +
  geom_boxplot() + 
  scale_fill_manual(name = "Is in top 3?",
                      labels = c("No", "Yes"),
                      values = hue_pal()(2)
                      )
  
```


###Customers with higher gross margin buy less frequently.
```{r}
  avg_diff_order_date_customers %>% 
    drop_na() %>% 
    filter_percent(mean_cost_of_part, 0.05) %>% 
  #filter(n_orders >= 10) %>% 
    #lm(mean_gm ~ log(avg_diff, 10), data = .) %>% summary()
  ggplot(aes(avg_diff, mean_cost_of_part)) +
  geom_point(alpha = 0.25) +
  scale_x_log10() +
 # scale_y_log10() +
  geom_smooth(method = "lm") +
  facet_wrap(~ customer_region)
```


###Scatterplot: average diff for order date ~ number of orders
```{r}
avg_diff_order_date_customers %>% 
  filter(!is.na(avg_diff) & avg_diff > 0) %>%
  #filter(n_orders < 10000) %>% 
  ggplot(aes(n_orders, avg_diff)) +
  geom_point(alpha = 0.5) + 
  scale_x_log10(labels = scales::comma) +
  scale_y_log10() +
  stat_smooth(method = "lm") +
  labs(
    x = "Number of orders",
    y = "Avg. time between two orders in days",
    title = "Log-log regression",
    subtitle = "Avg. time between two orders in days ~ Number of orders"
  )  %>% print()
```

### Idea for distribution: number of orders per customer
```{r}
#tikz(file = "ridge_avg_diff_order.tex", width = 2.5, height = 2.5)

avg_diff_order_date_customers %>% 
  filter(!is.na(customer_region)) %>% 
  filter(between(n_orders, 0, quantile(n_orders, 0.95))) %>% 
  ggplot(aes(n_orders)) +
  geom_density_ridges(aes(y = customer_region)) +
  labs(
    x = "Number of orders",
    y = NULL,
    title = NULL
  ) + 
  scale_x_log10() 
#dev.off()
``` 

### The most expensive orders
```{r}
order_date_by_customer %>% 
  slice_max(total_price, n = 100) %>% 
  count(customer_region, top_customer_group) %>% 
  ggplot(aes(n, top_customer_group)) +
  geom_segment(aes(yend = top_customer_group, xend = 0)) +
  geom_point(color = "orange", size = 2) +
  facet_wrap(~ customer_region, nrow = 3) +
  labs(
    x = "Number of orders",
    y = "Top customer group",
    title = "10000 most expensive orders",
    subtitle = "by customer region and top customer group"
  )
```

Star users from Asia have a large share in top 100k most expensive orders.

###Do users with smaller avg. difference between two events spend more on orders?
```{r}
avg_diff_order_date_customers %>% 
  filter(n_orders >= 10) %>% 
  filter(!is.na(customer_region)) %>% 
 # filter(between(gm_by_order, quantile(gm_by_order, 0.05), quantile(gm_by_order, 0.95))) %>% 
  ggplot(aes(total_price, avg_diff)) +
  geom_point(alpha = 0.1) +
  scale_x_log10(labels = scales::comma) + 
  scale_y_log10(labels = scales::comma) +
  stat_smooth(method = "lm") +
  labs(
    x = "Total price of all orders",
    y = "Avg. time between two orders in days",
    title = "Users with smaller time between orders time\ntend to spend more on orders"
  ) + 
  facet_wrap(~ customer_region, nrow = 3)
```

It's as expected: users with smaller time between order time tend to spend more 
money on orders.
Let's look 
###Star vs Other for avg diff for order date
```{r}
avg_diff_order_date_customers %>% 
  ggplot(aes(avg_diff, fill = top_customer_group)) +
  geom_histogram(aes(y = ..density..)) +
  scale_x_log10() +
  facet_wrap(~ top_customer_group) +
  labs(
    x = "Average difference in two consecutive orders in days",
    fill = "Top customer groups",
    title = "Difference between customer groups for avg. diff. in orders"
       ) +
  theme(legend.position = "bottom")
  
```


###boxplot for avg. diff. of orders by customer industries, faceted by customer region
```{r}
avg_diff_order_date_customers %>% 
  ggplot(aes(x = avg_diff)) +
  geom_density_ridges(aes(y = customer_industry)) +
  facet_wrap(~ customer_region)
```


###Hypothesis: Maybe more frequent customer get better deals?
```{r}
avg_diff_order_date_customers %>% 
 # filter(n_orders >= 20) %>% 
  #filter(max_order_date - min_order_date >= 100) %>% 
  filter(!is.na(customer_region)) %>% 
  filter(gm_by_order >= 0) %>% 
  # filter(between(gm_by_order,
  #                quantile(gm_by_order, 0.01),
  #                quantile(gm_by_order, 0.99))) %>% 
  ggplot(aes(gm_by_order, avg_diff)) +
  geom_point(alpha = 0.3) + 
  scale_y_log10() +
  stat_smooth(method = "lm") +
  facet_wrap(~ customer_industry)
```

Hypotheis:
does user get better deal if he buys more?
```{r}
avg_diff_order_date_customers %>% 
  filter(gm_by_order >= -1) %>% 
  filter_percent(total_qty, 0.4) %>% 
  ggplot(aes(gm_by_order, total_qty)) +
  geom_point()
```

### Check change of gross margin / unit price for items by last changed
```{r}
dat %>% 
  clean() %>% 
  filter(!is.na(price_last_modified_date_in_the_erp)) %>% 
  mutate(item_code = fct_lump_n(item_code, 10)) %>% 
  filter(item_code != "Other") %>% 
  filter(between(invoice_date, 
                 price_last_modified_date_in_the_erp - duration(1, units = "month"),
                 price_last_modified_date_in_the_erp + duration(1, units = "month")
                 )
         ) %>% glimpse

  
```

## Histogram of gross margin for product groups
```{r}
dat %>% 
  clean() %>% 
 filter(abs(gm) <= 10) %>%
  ggplot(aes(gm)) +
  geom_density_ridges(aes(y = product_group)) +
  labs(
    x = "gross margin"
  ) 
  #facet_wrap(~ product_group, scale = "free_y")
```

### Split gross margin for product groups in bins with eq observations

```{r}
dat %>% 
  clean() %>% 
  filter(product_group != "PC024") %>% 
  #sample_frac(0.1) %>% 
  group_by(product_group) %>% 
  mutate(gm = cut_number(gm, 10)) %>% 
  ungroup() %>% 
  group_by(product_group, gm) %>% 
  tally() %>% 
  ungroup() %>% 
  ggplot(aes(gm, n)) +
  geom_col() +
  facet_wrap(~ product_group, scale = "free")
```

### 
