---
title: "EDA - Part II"
author: "Josip Domazet"
date: "4/27/2021"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This markdown is supposed to be run after eda_part_1.Rmd.
It shows various column summaries with plots.

##Dataset structure 
```{r}
dat %>% 
  count(order_num, invoice_num) %>% 
  count(order_num) -> n_invoices_per_order
```


##Dataset inconsistencies
```{r}
dat %>% 
  filter(order_num == 1259712) %>% view()

# order_num == 514290 - order with 1 product, but 2 item lines  

# order_num == 4164713 1 product, 10 rows 

# order_num == 731696 - order with 1 product (item_code), but 4 item lines which were fully shipped with 4 separate invoices,
# completely same thing with 100205

# order_num == 100165 has 1 item_code, but 3 item lines,
# it's like the original order had two order lines with 
# same quantity and item_code

# item_code = 700627 doesn't have cost_of_part, only invoiced_price
# i've checked it after finding row with gross margin = 1
# TODO: check for items which have row with gross margin = 1
# and analyze whether they always have that gm



```

Check whether item line can have multiple products
```{r}
sample <-
  dat %>%
  slice_sample(n = 10000) %>% 
  select(order_num) %>% 
  distinct() %>% 
  pull(order_num)

order_line_multiple_products <-
  dat %>% 
  filter(order_num %in% sample) %>% 
  group_by(order_line_num) %>% 
  summarise(n_products = n_distinct(item_code))

multiple_products_order <-
  dat %>% 
  filter(order_num %in% sample) %>% 
  group_by(order_num) %>% 
  summarise(n_products = n_distinct(item_code),
            n_order_lines = n_distinct(order_line_num))
```

order_line_num = 1004214 is example of order line number where
we have two products.

##The most popular items
TRANSPORT cost on the invoice can be the reason for 2 item codes on
a invoice line

when cleaning data, transport item is deleted since transport doesn't have
manufacturing cost (cost_of_part == 0).

```{r}
{
  dat %>% 
    count(item_code) %>% 
    mutate(item_code = fct_reorder(item_code, n)) %>% 
    slice_max(n, n = 50, with_ties = FALSE) %>% 
    ggplot(aes(n, item_code)) +
    geom_col(fill = hue_pal()(2)[2], alpha = 0.6) +
    labs(
      x = "Number of rows",
      y = "Item code"
    ) +
    theme(text = element_text(size=6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
    ggsave(filename = "../plots/popular_items.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

We see some items are far more frequent than others.
We know some of those items are items related to transport.
Transport item code is identified by having invoiced_qty_shipped and
ordered_qty equal to zero. Furthermore, cost_of_part is 0.
It should also have manufacturing_region and manufacturing_location_code NA because
transportation is not manufactured.
Insight: product_family is PF000 for transportation and other 
not really manufactured things
### PF000
```{r}
dat %>% 
  filter(product_family == "PF000") %>% 
  count(item_code, sort = TRUE) %>% 
  slice_max(n, n =10)
```

Check their gross margins and ordered quantities
```{r}
dat  %>% 
  filter(product_family == "PF000") %>% 
  ggplot(aes(ordered_qty)) +
  geom_histogram() +
  scale_x_log10()
```

```{r}
dat  %>% 
  filter(product_family == "PF000") %>% 
  count(manufacturing_region)
```
All items with product_family == "PF000" have
NA for manufacturing region implying they are not really manufactured.

```{r}
dat  %>% 
  filter(product_family == "PF000") %>% 
  count(manufacturing_location_code)
```

I see that NA and N9 are the only two locations.
Maybe the company uses N9 for special kind of items.

```{r}
dat %>% 
  filter(product_family == "PF000") %>% 
  count(make_vs_buy, sort= TRUE)
```
Not very clear with make_vs_buy column.

```{r}
dat %>% 
  filter(product_family == "PF000") %>% 
  count(born_on_date, sort = TRUE)
```
The majority of PF000 items are without born_on_date which is another
argument for statement that they are not really manufactured.


Group by item codes, find *median* price and show a histogram
```{r}
dat %>% 
  filter(product_family == "PF000") %>% 
  group_by(item_code)  %>% 
  summarise(median_price = median(invoiced_price, na.rm = TRUE),
            n = n()) %>% 
  ggplot(aes(median_price)) +
  geom_histogram() +
  scale_x_log10()
```

```{r}
dat %>% 
  filter(product_family == "PF000") %>% 
  group_by(item_code)  %>% 
  summarise(median_price = median(invoiced_price, na.rm = TRUE),
            n = n()) %>% 
  ggplot(aes(n, median_price)) +
  geom_point() +
  scale_y_log10()
```

## make vs buy
```{r}
{
  dat %>% 
    count(make_vs_buy) %>% 
    mutate(make_vs_buy = fct_explicit_na(make_vs_buy)) %>% 
    mutate(make_vs_buy = fct_reorder(make_vs_buy, n)) %>% 
    ggplot(aes(n, make_vs_buy)) +
    #geom_col(fill = hue_pal()(2)[2], alpha = 0.6) +
    geom_col(aes(fill = make_vs_buy),
             color = "black",
             alpha = 0.8,
             show.legend = FALSE) +
    labs(
      x = "Number of rows",
      y = "Make vs buy"
    ) +
    theme(text = element_text(size=6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
  ggsave(filename = "../plots/make_vs_buy.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

## born-on-date
```{r}
{
  dat %>% 
  select(item_code, born_on_date) %>% 
  distinct() %>% 
  filter(born_on_date > ymd("1950-01-01")) %>% 
  ggplot(aes(born_on_date)) +
  geom_histogram(fill = hue_pal()(2)[2], alpha = 0.6, bins = 50,
                  size = .3, color = "black") +
  labs(
    x = "Born on date",
    y = "Number of items"
  ) +
  scale_x_date(date_breaks = "4 year", date_labels = "%Y") +
  theme(text = element_text(size=6),
  plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
      ggsave(filename = "../plots/born_on_date.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```
How many of items have two born on date?
There should be 3191 such items.
```{r}
dat %>% 
  select(item_code, born_on_date) %>% 
  distinct() %>% 
  group_by(item_code) %>% 
  summarise(n = n()) %>% 
  filter(n > 1) %>% 
  select(item_code) %>% distinct() -> items_with_multiple
```
2744 such items.
95.6 % items have only one born on date.

# Price and quantity
```{r}
{
  dat %>% 
    filter(invoiced_price > 0) %>% 
    filter(invoiced_price < 1089758016) %>% 
    #filter(between(invoiced_price,
    #              quantile(invoiced_price, 0.01, na.rm = TRUE),
    #             quantile(invoiced_price, 0.99, na.rm = TRUE))
    #    ) %>% 
    ggplot(aes(invoiced_price)) +
    geom_histogram(fill = hue_pal()(2)[2], alpha = 0.6, 
                    size = .25, color = "black") +
    scale_x_continuous(labels = scales::label_number_si()) +
    labs(
      x = "Invoiced price",
      y = "Number of rows"
    ) +
    scale_y_continuous(labels = scales::label_number_si()) +
    theme(text = element_text(size=6),
         plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
  ggsave(filename = "../plots/price_raw.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

Filter + outliers
```{r}
{
  dat %>% 
    filter(invoiced_price > 0) %>% 
    filter(between(invoiced_price,
                   quantile(invoiced_price, 0.001, na.rm = TRUE),
                   quantile(invoiced_price, 0.999, na.rm = TRUE))
    ) %>%
    ggplot(aes(invoiced_price)) +
    geom_histogram(fill = hue_pal()(2)[2], alpha = 0.6, 
                    size = .25, color = "black") +
    scale_x_continuous(labels = scales::label_number_si()) +
    labs(
      x = "Invoiced price",
      y = "Number of rows"
    ) +
    scale_y_continuous(labels = scales::label_number_si()) +
    theme(text = element_text(size=6),
          plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
        ggsave(filename = "../plots/price_filtered_linear.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

```{r}
{
  dat %>% 
  filter(invoiced_price > 0) %>% 
    filter(invoiced_price <  1089758016.0) %>% 
  # filter(between(invoiced_price,
  #              quantile(invoiced_price, 0.01, na.rm = TRUE),
  #             quantile(invoiced_price, 0.99, na.rm = TRUE))
  #    ) %>%
  ggplot(aes(invoiced_price)) +
  geom_histogram(fill = hue_pal()(2)[2], alpha = 0.6,
                 size = .25, color = "black") +
  scale_x_continuous(trans = scales::log10_trans(), 
                     labels = scales::comma_format(accuracy = 0.001),
                     breaks = c(0.001, 0.1, 1, 10, 10000)) +
  labs(
    x = "Invoiced price",
    y = "Number of rows"
  ) +
  scale_y_continuous(labels = scales::label_number_si()) +
  theme(text = element_text(size=6),
        plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
        ggsave(filename = "../plots/price_filtered_log.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

## Cost of part
```{r}
{
  dat %>% 
  filter(cost_of_part > 0) %>% 
  filter(between(cost_of_part,
               quantile(cost_of_part, 0.01, na.rm = TRUE),
              quantile(cost_of_part, 0.99, na.rm = TRUE))
     ) %>%
  ggplot(aes(cost_of_part)) +
  geom_histogram(fill =hue_pal()(2)[2], alpha = 0.75) +
  scale_x_continuous(trans = scales::log10_trans(), labels = scales::label_number_si()) +
  labs(
    x = "cost_of_part",
    y = "Number of rows"
  ) +
  scale_y_continuous(labels = scales::label_number_si()) +
  theme(text = element_text(size=6),
        plot.margin=grid::unit(c(2, 0.3, 2, 2), "mm"))
  } %>% 
        ggsave(filename = "../plots/cost_of_part_filtered_log.pdf", 
         width = 6,
         height = 6,
         units = "cm",
         dpi = 300,
         device = pdf)
```

## Cost of labor
```{r}
  dat %>% 
  filter(labor_cost_of_part > 0) %>% 
  filter(between(labor_cost_of_part,
               quantile(labor_cost_of_part, 0.01, na.rm = TRUE),
              quantile(labor_cost_of_part, 0.99, na.rm = TRUE))
     ) %>%
  ggplot(aes(labor_cost_of_part)) +
  geom_histogram(fill =hue_pal()(2)[2], alpha = 0.75) +
  labs(
    x = "labor_cost_of_part",
    y = "Number of rows"
  ) +
  scale_y_continuous(labels = scales::label_number_si()) +
  scale_x_log10(labels = function(v) sprintf("%.3f", as.numeric(v)))
  
```

## Material cost
```{r}
  dat %>% 
  filter(material_cost_of_part > 0) %>% 
  filter(between(material_cost_of_part,
               quantile(material_cost_of_part, 0.01, na.rm = TRUE),
              quantile(material_cost_of_part, 0.99, na.rm = TRUE))
     ) %>%
  ggplot(aes(material_cost_of_part)) +
  geom_histogram(fill =hue_pal()(2)[2], alpha = 0.75) +
  labs(
    x = "material_cost_of_part",
    y = "Number of rows"
  ) +
  scale_y_continuous(labels = scales::label_number_si()) +
  scale_x_log10(labels = function(v) sprintf("%.3f", as.numeric(v)))
```
## Overhead
```{r}
  dat %>% 
  filter(overhead_cost_of_part > 0) %>% 
  filter(between(overhead_cost_of_part,
               quantile(overhead_cost_of_part, 0.01, na.rm = TRUE),
              quantile(overhead_cost_of_part, 0.99, na.rm = TRUE))
     ) %>%
  ggplot(aes(overhead_cost_of_part)) +
  geom_histogram(fill =hue_pal()(2)[2], alpha = 0.75) +
  labs(
    x = "overhead_cost_of_part",
    y = "Number of rows"
  ) +
  scale_y_continuous(labels = scales::label_number_si()) +
  scale_x_log10(labels = function(v) sprintf("%.3f", as.numeric(v)))
```

```{r}
{
  dat %>% 
  filter(if_any(ends_with("cost_of_part"), ~ . > 0)) %>% 
  filter(if_all(ends_with("cost_of_part"), ~ between(.,
                                                     quantile(., 0.001, na.rm=T),
                                                     quantile(., 0.999, na.rm=T)))) %>% 
  pivot_longer(cols = ends_with("cost_of_part"), names_to = "cost_variant",
               values_to = "value") %>% 
  ggplot(aes(x = value, y = cost_variant, fill = cost_variant)) + 
  geom_density_ridges(show.legend = FALSE, alpha = 0.7) + 
  scale_x_continuous(trans = scales::log10_trans(),
                     labels = function(v) sprintf("%.3f", v),
                     breaks = c(0.01, 1, 10, 1000, 10000)) +
  labs(
    x = "Value",
    y = "Cost component"
  ) + 
    theme(text = element_text(size=6),
         plot.margin=grid::unit(c(2, 1, 2, 2), "mm"))
} %>% 
        ggsave(filename = "../plots/cost_components_ridge.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

## Gross margin

Bin into bins with the same number of observation
```{r}
dat %>% 
  #filter(!is.na(gm)) %>% 
  mutate(gm_bin = case_when(
    gm < 0 ~ "negative",
    between(gm, 0, 1) ~ "normal values",
    between(gm, 1, +Inf) ~ "above 1",
    TRUE ~ "NA"
  )) %>% 
  count(gm_bin) %>% 
  mutate(gm_bin = factor(gm_bin, 
                         levels = c("negative", "normal values", "above 1", "NA"))) %>% 
  ggplot(aes(gm_bin, n, fill = gm_bin, color = gm_bin)) +
  geom_segment(aes(xend = gm_bin, yend = 0)) +
  geom_point(size = 2) +
  scale_y_continuous(labels = scales::label_number_si()) +
  labs(
    x = "Gross margin bin",
    y = "Number of rows"
  ) +
  scale_fill_manual(
    values = c("negative" = hue_pal()(2)[1],
               "normal values" = hue_pal()(2)[2],
               "above 1" = hue_pal()(2)[1],
               "NA" = hue_pal()(2)[1])
  ) +
    scale_color_manual(
    values = c("negative" = hue_pal()(2)[1],
               "normal values" = hue_pal()(2)[2],
               "above 1" = hue_pal()(2)[1],
               "NA" = hue_pal()(2)[1])
  )
```


Histogram
```{r}
{
  dat %>% 
  #filter(invoiced_price > 0) %>% 
  filter(between(gm, 0, 1.00)) %>% 
  # invoiced_price == 0 is mostly for transportation
  # but cost_of_part == 0 makes no sense
  ggplot(aes(gm)) +
  geom_histogram(fill =hue_pal()(2)[2], alpha = 0.75,
                 size = .25, color = "black") +
  labs(
    x = "Gross margin",
    y = "Number of rows"
  ) +
    theme(text = element_text(size=6),
          plot.margin = grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
    ggsave(filename = "../plots/gm_between_0_1.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

It looks kinda normally distributed, except that we have 
very big count at value of 1.00
```{r}
{dat %>% 
  filter(gm == 1) %>%
  filter(between(invoiced_price, 
                 quantile(invoiced_price, 0.01, na.rm = TRUE),
                 quantile(invoiced_price, 0.09, na.rm = TRUE)
  )
  ) %>% 
  ggplot(aes(invoiced_price)) +
  geom_histogram(bins = 50,
                 fill = hue_pal()(2)[2], alpha = 0.75,
                 size = .25, color = "black") +
  labs(
    x = "Invoiced price",
    y = "Number of rows"
  ) +
  theme(text = element_text(size=6),
        plot.margin = grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
          ggsave(filename = "../plots/rows_with_gm_1.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```


##Ridge density of invoiced price for gross margin (5 bins)
Boxplot/ridge density for gross margin binned into 
bins spanning equal range
This is with **linear scale**
```{r}
{
  dat %>% 
    filter(gm > 0 & gm < 1) %>% 
    mutate(gm_bin = ggplot2::cut_interval(gm, n = 5)) %>% 
    filter(invoiced_qty_shipped > 0) %>% 
    group_by(gm_bin) %>% 
    filter(between(invoiced_price, 
                   quantile(invoiced_price, 0.05, na.rm = TRUE),
                   quantile(invoiced_price, 0.95, na.rm = TRUE))) %>% 
                   ggplot(aes(invoiced_price, gm_bin, fill = gm_bin)) +
                     geom_density_ridges(
                       show.legend = TRUE,
                       alpha = 0.75) +
                      scale_x_log10(labels = scales::label_number_si(accuracy = 0.01),
                                    breaks = c(0.01, 0.1, 1, 10, 100, 1000, 10000)) +
                     labs( 
                       x = "Invoiced price",
                       y = "Number of rows"
                     ) +
                     theme(text = element_text(size=6),
                           plot.margin = grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
  ggsave(filename = "../plots/prices_by_gm_bins_equal_interval_5_ridge.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
```

This is for **log scale**
```{r}
{dat %>% 
    filter(between(gm, 0, 1)) %>% 
    mutate(gm_bin = ggplot2::cut_interval(gm, n = 5)) %>% 
    group_by(gm_bin) %>% 
    filter(between(invoiced_price, 
                   quantile(invoiced_price, 0.05, na.rm = TRUE),
                   quantile(invoiced_price, 0.95, na.rm = TRUE))) %>% 
                   ggplot(aes(invoiced_price, gm_bin)) +
                   geom_boxplot(fill = hue_pal()(2)[2]) +
    scale_x_log10(labels = scales::label_number_si()) 
                     geom_density_ridges(fill = hue_pal()(2)[2], alpha = 0.75) +
                     labs( 
                       x = "Invoiced price",
                       y = "Number of rows"
                     ) +
    scale_x_log10(labels = scales::label_number_si()) +
                     theme(text = element_text(size=6),
                           plot.margin = grid::unit(c(2, 0.3, 2, 2), "mm"))
} %>% 
  ggsave(filename = "../plots/prices_by_gm_bins_equal_interval_log.pdf", 
         width = 8,
         height = 8,
         units = "cm",
         dpi = 300,
         device = pdf)
